
# Author's Note {-}

This master's thesis has been written in *R Markdown* [@Allaire2016] in order to make it *transparent* and *reproducible* for the reader. All ressources are available on my Github [account](https://github.com/pkinif/Thesis).  The latter is organised following the methodology of @Gandrud2013b. Each section of this thesis corresponds to a R Markdown file in the *Child* folder. The *Child/ThesisSkeleton.Rmd* file is the "parent" document which merges all the "child" documents into a consolidated pdf document, namely the one you are reading. The *Child/Analysis* sub-folders contains a list of R script (i.e. Make files) whose outputs are saved into the following sub-folders *Child/Analysis/DataBase*.

The platform I have used is [Rstudio](https://www.rstudio.com/) which is an open source software for R. Here is the information of my session : 


```{r echo = FALSE, message = FALSE, error = FALSE, warning = FALSE}


# Packages loading 

rm(list=ls()) #Removes all items in the R environment
if (!require("plm")) install.packages("plm")
library(plm) 
if (!require("dplyr")) install.packages("dplyr")
library(dplyr) 
if (!require("data.table")) install.packages("data.table")
library(data.table)
if (!require("stargazer")) install.packages("stargazer")
library(stargazer)
if (!require("Hmisc")) install.packages("Hmisc")
library(Hmisc)
if (!require("purrr")) install.packages("purrr")
library(purrr)
if (!require("lattice")) install.packages("lattice")
library(lattice)
if (!require("survival")) install.packages("survival")
library(survival)
if (!require("ggplot2")) install.packages("ggplot2")
library(ggplot2)
if (!require("xts")) install.packages("xts")
library(xts) 
if (!require("PerformanceAnalytics")) install.packages("PerformanceAnalytics")
library(PerformanceAnalytics) 
if (!require("tibble")) install.packages("tibble")
library(tibble) 
if (!require("tidyquant")) install.packages("tidyquant")
library(tidyquant) 
if (!require("car")) install.packages("car")
library(car)
if (!require("ggpubr")) install.packages("ggpubr")
library(ggpubr)
if (!require("xtable")) install.packages("xtable")
library(xtable)
if (!require("rvest")) install.packages("rvest")
library(rvest) 
if (!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
if (!require("rlist")) install.packages("rlist")
library(rlist)
if (!require("RCurl")) install.packages("RCurl")
library(RCurl)
if (!require("utils")) install.packages("utils")
library(utils) #to dowload db
if (!require("tibble")) install.packages("tibble")
library(tibble) 
if (!require("lubridate")) install.packages("lubridate")
library(lubridate) 
if (!require("tidyr")) install.packages("tidyr")
library(tidyr)
if (!require("plyr")) install.packages("plyr")
library(plyr)
```


```{r tidy = TRUE}
sessionInfo()
```

