
# Data Description

```{r echo = FALSE, warning = FALSE, message = FALSE, error = FALSE}
if (!require("utils")) install.packages("utils")
if (!require("dplyr")) install.packages("dplyr")
if (!require("plm")) install.packages("plm")
if (!require("xtable")) install.packages("xtable")
if (!require("stargazer")) install.packages("stargazer")
library(stargazer)
library(xtable)
library(plm)
library(utils)
library(dplyr)

# I dowload my DB with read.csv
DbLag1<-data.frame(read.csv("Analysis/DataBase/DataSynchronization/Lag1.csv", sep = ",",stringsAsFactors=FALSE, header = TRUE ))

```


## Overview

The starting point of the data collection process was the Newsweek Green Rankings (i.e. NGR). This ranking has assessed the world’s largest publicly-traded companies in the US and in the world since 2009. It has been developed through a collaboration between Newsweek, Corporate Knights Capital, HIP Investor Inc and leading sustainability minds from nongovernmental organizations and the academic and accounting communities. 

The NGR attributes an overall Green Score (i.e. GS) to companies. This score is based on a weighted average of key performance indicators (i.e. KPI). This study uses these KPI to approach both process-based and outcome-based CEP of the 500 largest publicly-traded companies in the US. As a result of making a transition to a 100% rules-based approach, the methodology for the 2014 NGR differs considerably from the framework used in the 2012 NGR. Therefore, this study considers only the [`2014`](http://www.newsweek.com/green/worlds-greenest-companies-2014), [`2015`](http://www.newsweek.com/green-2015/top-green-companies-world-2015) and [`2016`](http://www.newsweek.com/green-2016/top-green-companies-world-2016) NGR. Among those three rankings and of the 500 US companies, 405 companies were listed each year.


Even though the NGR were published in 2014, 2015 and 2016, each company is evaluated based on the 2012, 2013 and 2014 company data. Therefore, measures for CFP will be based on the 2012, 2013 and 2014 fundamental data. Financial data have been collected on [`Morningstar`](http://www.morningstar.be/be/default.aspx), [`Stockpup`](http://www.stockpup.com/) and [`Ycharts`](https://ycharts.com/) using [`R`](https://cran.r-project.org/) technology. The data collection process is described in *"[Appendix A: Database Construction]"*. Of the 405 initial companies, a total of 12 were dropped because of missing data. The final sample includes 393 publicly-traded companies in the US covering the period from 2012 till 2014 inclusively. 

\autoref{VarDef} gives an overview of the variables of the econometric model. Following sub-sections deeply explain each variable.
```{r echo = FALSE, message = FALSE, warning = FALSE,  results='asis', error = FALSE}

Variables <- c("ROA", "Tobin's Q", "CaP", "WaP", "WastP", "SPL", "STC", "AS", "Leverage", "Growth", "Firm Size", "Industry")

Description <- c("Earnings before interest over total firm assets",
                 "The ratio of a firm’s market value to the replacement cost of its assets",
                 "Revenue (USD) / Total Greenhouse Gas Emissions (CO2)",
                 "Revenue (USD) / Total water (m3)",
                 "Revenue (USD) / [Total waste generated (metric tons) – waste recycled/reused (tons)]",
                 "A mechanism to link the remuneration of any member of a company's senior executive team with the achievement of environmental performance targets. Dummy variable which equals 1 if such a link exists and 0 otherwise",
                 "Refers to the existence of a committee at the Board of Directors level whose mandate is related to the sustainability of the company, including but not limited to environmental matters. Dummy variable which equals 1 if such a committee exists and 0 otherwise",
                 "Refers to the case where a company provides evidence that the latest reported environmental metrics were audited by a third party. Dummy variable which equals 1 if such evidence exist and 0 otherwise",
                 "The ratio of long-term debt to common shareholders' equity (shareholders equity minus preferred equity)",
                 "Net margin, namely the ratio of earnings to revenue",
                 "Natural logarithm of total assets",
                 "Global Industry Classification Standard (i.e. GICS) of the firm. The variable takes a value from 1 to 10 where 1 = Consumer Discretionary, 2 = Consumer Staples, 3 = Energy, 4 = Financials, 5 = Health Care, 6 = Industrials, 7 = Information Technology, 8 = Materials, 9 = Pharmaceuticals / Biotechnology, 10 = Telecommunication Services and 11 = Utilities")

Table <- as.data.frame(cbind(Variables, Description))
colnames(Table) <- c("Variables", "Description")

table <- xtable(Table, caption = "Variables Description", label ="VarDef", align = c("l","p{3cm}", "p{10cm}"))

print.xtable(table, comment=FALSE, caption.placement = "top", table.placement = "h", hline.after = c(-1,-1,0,12))

```


## Dependent Variables

```{r echo = FALSE, error = FALSE, message = FALSE}
### Skweness measurement

if (!require("moments")) install.packages("moments")
library(moments)

Q <- na.omit(DbLag1$TobinsQ)
SkwenessQ <- round(skewness(Q), digits = 2)
```

Regarding dependent variables, @EndrikatMakingsenseconflicting2014 claimed that accounting-based measures (e.g. Return On Asset, Return On Equity, Return On Sales) capture immediate impacts and can be used as a proxy to measure short-term CFP while market-based measures (e.g. Tobin's Q, market capitalization, market to book value) integrate estimations of firm’s future prospects and can be better used as a proxy for long-term CFP. Among scholars which used both measures simultaneously, ROA and Tobin's Q are the most frequent [@Lioui2012; @Cavaco2014; @Muhammadrelationshipenvironmentalperformance2015; @Delmas2015; @Semenova2016; @ManriqueAnalyzingEffectCorporate2017]. Therefore, this study uses ROA and Tobin's Q as proxies for both short-term and long-term CFP.

*ROA* is a standard accounting measure of financial performance, which is calculated by dividing earnings before interest by total firm assets. ROA gives information about how a company can transform assets into profit. 

*Tobin's Q* is defined as the ratio of the market value of a firm to the replacement cost of its assets [@Chung1994]. Firms displaying Tobin’s Q greater than one are judged as using scarce resources effectively and those with Tobin’s Q less than one as using resources poorly [@Lewellen1997]. In other words, investors prefer companies with Tobin's Q superior to one. Due to the complexity of calculating the replacement cost of a firm, the literature has described several attempts to approximate Tobin's Q [@Perfect1994]. This study collected Tobin's Q data directly on `Ycharts`. This financial data platform uses the simple approximation of @Chung1994 which is summarized in equation \ref{Chung}. Due to a high right-skew (i.e. skewness = `r SkwenessQ `), I use a natural logarithm transformation to normalize the distribution of Tobin's Q [@Honaker2011a].

\begin{equation}
Tobin's Q = \frac{MVE + PS + DEBT}{TA}
\label{Chung}
\end{equation}


where \(MVE\) is the product of a firm's share price and the number of common stock shares outstanding, \(PS\) is the liquidating value of the firm's outstanding preferred stock, \(DEBT\) is the value of the firm's short-term liabilities net of its short-term assets, plus the book value of the firm's long-term debt and \(TA\) is the book value of the total assets of the firm.

## Independent Variables


Both process-based and outcome-based CEP has been measured with the KPI of the NGR. I use “Sustainability Pay Link”, “Sustainability Themed Committee”, and “Audit Score” as proxies for process-based CEP and "Carbon Productivity", "Water Productivity" and "Waste Productivity" as proxies for outcome-based CEP\footnote{The NGR has another KPI that captures outcome-based CEP (i.e. Energy Productivity). Due to multicollinearity concern (Variance Inflation Factor superior to 5 for both Energy and Carbon Productivity),  I do not consider this KPI into the econometric model.}.

*A Sustainability Pay Link* (i.e. SPL) is a mechanism to link the remuneration of any member of a company’s senior executive team with the achievement of environmental performance targets. A score of 1 accrues to the company when such a link exists and a score of 0 otherwise.

*A Sustainability Themed Committee* (i.e. STC) refers to the existence of a committee at the board of directors level whose mandate is related to the sustainability of the company, including but not limited to environmental matters. A score of 1 accrues to the company when such a link exists and a score of 0 otherwise.

*An Audit Score* (i.e. AS) refers to the case where a company provides evidence that the latest reported environmental metrics were audited by a third party. A score of 1 accrues to the company if such an audit has been performed, and a score of 0 otherwise.

*Carbon Productivity* (i.e. CaP), *Water Productivity* (i.e. WatP) and *Waste Productivity* (i.e. WastP) are calculated through equation \ref{CaP}, \ref{WatP} and \ref{WastP}. 


\begin{equation}
CaP_{it} = \frac{Revenue_{it}}{TGGE_{it}}
\label{CaP}
\end{equation}

\begin{equation}
WatP_{it} = \frac{Revenue_{it}}{TW_{it}}
\label{WatP}
\end{equation}

\begin{equation}
WastP_{it} = \frac{Revenue_{it}}{(TWG_{it} - TWRR_{it})}
\label{WastP}
\end{equation}

where \(Revenue_{it}\) is the total revenue in \(USD\), \(TGGE_{it}\) is the total greenhouse gaz emissions in \(CO_{2}\), \(TW_{it}\) is the total water in \(m_{3}\), \(TWG_{it}\) is the total waste generated in metric tons and \(TWRR\) is the total waste recycled and reused in metric tons.

## Control Variables

Scholars argue that misspecified models may be a reason for the inconsistency of the empirical results in the CEP-CFP nexus [@Telle2006; @McWilliams2006; @Surroca2010]. To improve the construct and to avoid the endogeneity issue due to omitted variables [@Roberts2013], @EndrikatMakingsenseconflicting2014 highlighted some potential determinants of the relationship between CEP and CFP: firm size, industry sector, and capital structure. In a meta-analysis study, @Ludecadedebatenexus2014 argued that growth rate is equally important. This study uses these four determinants as control variables.

The common way to approach *firm size* is to use the natural logarithm of total assets [@Delmas2015; @MiroshnychenkoGreenpracticesfinancial2017]. To approach the company *industry sector*, I use the Global Industry Classification Standard (GICS) \footnote{The GICS classification is composed of eleven industry sectors, namely: Consumer Discretionary, Consumer Staples, Energy, Financials, Health Care, Industrials, Information Technology, Materials, Pharmaceuticals / Biotechnology, Telecommunication Services and Utilities.}. *Capital structure* is interpreted here as the financial leverage, namely the debt to equity ratio. The latter is measured as the ratio of long-term debt to common shareholders’ equity (shareholders equity minus preferred equity). The *growth rate* is approached through the net margin (i.e. the ratio of earnings to revenue).

 















