---
output:
  pdf_document
header-includes:
- \usepackage{amsmath}
---
```{r echo =FALSE, message = FALSE, error = FALSE}
if (!require("dplyr")) install.packages("dplyr")
library(dplyr)
if (!require("plm")) install.packages("plm")
library(plm)
if (!require("stargazer")) install.packages("stargazer")
library(stargazer)
# I download my database 

DB_Lag1<-data.frame(read.csv2("Analysis/DataBase/Lag_1.csv", sep = ";",stringsAsFactors=FALSE, header = TRUE ))

```

# Methodology

## Econometric model

<!--
... Deal with methodology to test H1 ..... **To be defined**

-->


Panel data is a common approach to adress the CFP-CEP nexus [@Albertini2013]. Panel data, also called longitudinal data or cross-sectional time-series data include observations on N cross section units (i.e., firms) over T time-periods [@Hsiao2007a]. As panel data analysis use variation in both these dimensions, it is considered to be one of the most efficient analytical methods for data [@DimitriosAsteriou2006]. It usually contains more degrees of freedom, less collinearity among the variables, more efficiency and more sample variability than one-dimensional method (i.e.cross-sectional data and time series data) giving a more accurate inference of the parameters estimated in the model [@Hsiao2007, @HsiaoChapitrePanelData2014]. @Roberts2013 also argued that using panel data offer a partial, but by no means complete and costless, solution to the problem of omitted variables in model, namely the most common causes of endogeneity in empirical corporate finance. Consequently this study use equation \ref{EconometricModel} to test the combined effect of process and outcome-based CEP on CFP.

\begin{equation}
\centering
\begin{aligned}
Y_{it+1} & = & \beta_{0} + \beta_{1} (SPL_{it}) \\
&& + {} \beta_{2} (STC_{it}) + \beta_{3} (A_{it}) \\
&& + {} \beta_{4} (EnP_{it})  + \beta_{5} (CaP_{it}) \\
&& + {} \beta_{6} (WatP_{it}) + \beta_{7} (WastP_{it}) \\ 
&& + {} (Controls_{it}) + \varepsilon_{it}
\label{EconometricModel}
\end{aligned}
\end{equation}


where \(Y_{it+1}\) is a proxy of CFP measured as ROA or Tobin's Q, \(SPL_{it}\) is a proxy for a firm's sustainability pay link, \(STC_{it}\) is a proxy for a firm's sustainability themed commitment, \(A_{it}\) is a proxy for a firm's audit score, \(EP_{it}\) is a proxy for a firm's energy productivity, \(CP_{it}\) is a proxy for a firm's carbon productivity, \(WatP_{it}\) is a proxy for a firm's water productivity, \(WasP_{it}\) is a proxy for a firm's waste productivity, \(Controls_{it}\) is a vector of control variables that includes firm size, industry sector, financial risk, R&D activities, advertising intensity and capital structure and lastly \(\varepsilon_{it}\) which is the error term.

Panel data setting implies that endogeneity occurs in cases where the independent variable in a regression model is correlated with the error term, or due to simultaneous causality between the dependent and the independent variable [@Sanchez-Ballesta2007, @Biorn2008, @Roberts2013]. Consequently, the presence of endogeneity implies that the fourth and fifth assumptions of OLS\footnote{Five assumptions are required to produce consistent estimators with OLS : (i) a random sample of observations on \(y\) and \((x_{1},...., x_{n})\), (ii) a mean zero error term, (iii) no linear relationship among the explanatory variables, (iv) an error term that is uncorrelated with each explanatory variables and (v) an error term with zero mean conditional on the explanatory variables.} are violated and scholars have to used a different method to produce consistent estimators [@Wooldridge2008, @Roberts2013]. Recent meta-analysis provided evidences that the CFP-CEP nexus is characterized by a bidirectional causality [@Orlitzky2001, @Orlitzky2003, @Wu2006, @Albertini2013, @Dixon-Fowler2013, @EndrikatMakingsenseconflicting2014, @Ludecadedebatenexus2014, @WangMetaAnalyticReviewCorporate2016, @Busch2018]. In order to adress potential endogeneity problems in my model, firstly, I have lagged observations in dependent and control variables one year behind financial performance. This method allows to increase the confidence of the direction of the relationship [@Hart1996, @Delmas2015, @MiroshnychenkoGreenpracticesfinancial2017] and *in fine* reduce the simultaneity bias. Secondly, given that the standard Hausman test had rejected the null hypothesis of random effect (see Annex... for results of the test) I use a fixed effect model to regress \ref{EconometricModel}. According to @Roberts2013, fixed effect model ameliorate endogeneity concerns. 



<!--
Motivations to use one time lag - citation from [@Albertini2013]: 

> Hart and Ahuja (1996) argue that there is a time lag between the initiation of emission reduction efforts and the realization of bottom line benefits. First, pollution prevention requires up-front investment in training and equipment. Second, it takes time to gain reduction because internal reorganization and renegotiation of supply and waste disposal contracts may be required (Hart & Ahuja, 1996). Evidence also suggests that in the early stages of pollution prevention there is a great deal of “low-hanging fruit”—easy and inexpensive behavioural and material changes that result in large emission reductions relative to costs (Hart, 1994; Rooney, 1993). As the firm’s environmental performance improves, further reductions in emissions become progressively more difficult, requiring more significant change in processes or even entirely new production technology (Russo & Fouts, 1997). Some studies have collected data on a longitudinal perspective (more than 1 year) in order to take into account the long-term payback of environmental management strategies, while others have collected data on a short period of time (1 year and less). Analysing the relationship between CEM and CFP during a short period of time implies that the researcher intends to prove that the environmental management influences regularly and at any time the financial profitability of the firm. Yet the natural and organizational environments are different because of the time markers of their respective materialities, such as short term for the financial profitability and very long term for the environmental issue (Bansal & Knox-Hayes, 2013). Thus, we can argue that the longitudinal characteristic of the studies might explain part of the variation in the results regarding the relationship between CEM and CFP. **NB: the hypothese had been verified : The relationship between CEM and CFP is significantly stronger for non-longitudinal studies (0.13) than for longitudinal studies (0.07)**

-->


```{r echo = FALSE, error = FALSE, message = FALSE, results = 'hide'}
if (!require("stargazer")) install.packages("stargazer")
library(stargazer)

if (!require("xtable")) install.packages("xtable")
library(xtable)

# Fixed Model

FixedTobinsQ <- plm(TobinsQ ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore + EnergyProductivity + CarbonProductivity + WaterProductivity + WasteProductivity + Leverage + NetMargin + FirmSize + Industry, data=DB_Lag1, index=c("Companies", "YearFinancialIndicator"), model="within")

FixedRoa <- plm(ROA ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore + EnergyProductivity + CarbonProductivity + WaterProductivity + WasteProductivity + Leverage + NetMargin + FirmSize + Industry, data=DB_Lag1, index=c("Companies", "YearFinancialIndicator"), model="within")

# Random Model

RandomTobinsQ <- plm(TobinsQ ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore + EnergyProductivity + CarbonProductivity + WaterProductivity + WasteProductivity + Leverage + NetMargin + FirmSize + Industry, data=DB_Lag1, index=c("Companies", "YearFinancialIndicator"), model="random")

RandomRoa <- plm(ROA ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore + EnergyProductivity + CarbonProductivity + WaterProductivity + WasteProductivity + Leverage + NetMargin + FirmSize + Industry, data=DB_Lag1, index=c("Companies", "YearFinancialIndicator"), model="random")

# Hausmann Test

PvalRoa <- round(phtest(FixedTobinsQ,RandomTobinsQ)$p.value, digits = 4)
HausmanTobinsQ <- cbind("Model 5",PvalRoa)

PvalTobinsQ <- round(phtest(FixedRoa,RandomRoa)$p.value, digits = 4)
HausmanRoa <- cbind("Model 6",PvalTobinsQ)


#summary in table

HausmanTable <- rbind(HausmanRoa, HausmanTobinsQ)
colnames(HausmanTable) <- c("Model","p-value")

#xtable(HausmanTable, caption = "Hausman Test Result", label = "Hausman", align = "rrr")

stargazer(HausmanTable, summary = FALSE, table.placement = "h", type="latex", label = "Hausman", title = "Hausman Test p-value", header = FALSE)

```

## Sensitivity Analysis

For the sensitivity analysis, let's make as [@MiroshnychenkoGreenpracticesfinancial2017], namely take ROE as an other accounting based indicators and I need to find an other market based indicator.