---
output:
  pdf_document
---
This appendix presents the R code used to identify and remove outliers from the database. This R script is the one contains in the makefile `Analysis/DataBase/MakeFile_RemoveOutliers_Lag1.Rmd`. This step had been repeated three times : (i) when dependent variables were lagged one year (see section: *"[The impact of CEP on CFP]"*) and (ii) two years behind others variables and (iii) when the GreenScore variable was the only independent variable considered into the econometric model (see section: [Sensitivity Analysis]).  


```{r message = FALSE, size = 'smallsize', error = FALSE, warning = FALSE, results = 'asis', tidy = TRUE, comment = FALSE, tidy.opts=list(blank=FALSE, width.cutoff=55)}
# Packages loading 
if (!require("dplyr")) install.packages("dplyr")
library(dplyr)
if (!require("data.table")) install.packages("data.table")
library(data.table)
if (!require("formatR")) install.packages("formatR")
library(formatR)
if (!require("highlight")) install.packages("highlight")
library(highlight)

```

```{r message = FALSE, tidy.opts=list(blank=FALSE, width.cutoff=55), error = FALSE, warning = FALSE, results = 'asis', tidy = TRUE, comment = FALSE}
# Database Loading 
path <- "Analysis/DataBase/DataSynchronization/Lag1.csv"
Lag1 <- read.csv(
  file = path, 
  header = TRUE, 
  stringsAsFactors = FALSE)

```


```{r message = FALSE, error = FALSE, warning = FALSE, tidy.opts=list(blank=FALSE, width.cutoff=55),  results = 'asis', tidy = TRUE, comment = FALSE}
# Select only variables that I need for my model
ModelLag1 <- Lag1 %>% 
  select(c(YearIndex,
           CompaniesIndex,
           Roa,
           TobinsQ,
           DebtToEquityRatio,
           NetMargin,
           TotalAssets,
           GicsClassification,
           CarbonProductivity,
           WaterProductivity,
           WasteProductivity,
           SustainabilityPayLink,
           SustainableThemedCommitment,
           AuditScore
           ))

# I transform the "TotalAssets" column into FirmSize using the log of TotalAssets 
ModelLag1$TotalAssets <- log10(ModelLag1$TotalAssets)

# I use the natural log for TobinsQ
ModelLag1$TobinsQ <- log10(ModelLag1$TobinsQ)

# I rename some columns
ModelLag1 <- ModelLag1 %>% 
  setnames(old = 
             c("DebtToEquityRatio", 
               "TotalAssets", 
               "GicsClassification", 
               "NetMargin"), 
           new = 
             c("Leverage", 
               "FirmSize", 
               "Industry", 
               "Growth"))

# I define my models in lm as cooks.distance do not support plm object
Roa <-lm(Roa ~ SustainabilityPayLink +
           SustainableThemedCommitment + 
           AuditScore + 
           CarbonProductivity + 
           WaterProductivity + 
           WasteProductivity + 
           FirmSize + 
           Growth + 
           Leverage + 
           Industry, 
         data = ModelLag1)

TobinsQ<-lm(TobinsQ ~ SustainabilityPayLink + 
              SustainableThemedCommitment + 
              AuditScore + 
              CarbonProductivity + 
              WaterProductivity + 
              WasteProductivity + 
              FirmSize + 
              Growth + 
              Leverage + 
              Industry, 
            data = ModelLag1)

# I calculate my cooks distance (i.e. D)
cooksdRoa <- cooks.distance(Roa)
cooksdTobinsQ <- cooks.distance(TobinsQ)

# I extract rows considered as influential (i.e. observations whose D > 4 * means) and I print them for the reader.
influentialRoa <- as.numeric(names(cooksdRoa)[(cooksdRoa > 4*mean(cooksdRoa, na.rm=T))]) 
influentialRoa
influentialTobin <- as.numeric(names(cooksdTobinsQ)[(cooksdTobinsQ > 4*mean(cooksdTobinsQ, na.rm=T))])
influentialTobin
```

```{r echo = TRUE, eval = FALSE, error = FALSE, tidy.opts=list(blank=FALSE, width.cutoff=55), message = FALSE, warning = FALSE, comment = FALSE, tidy = TRUE}

#I remove outliers and create two new dataframes that I write in my folders
TobinsQ_Db <- ModelLag1[-c(influentialTobin),]
p <- "Analysis/DataBase/DataSynchronization/NoOutliersLag1/TobinsQ.csv"
write.csv(
  TobinsQ_Db,
  file = p)

p <- "Analysis/DataBase/DataSynchronization/NoOutliersLag1/Roa.csv"
Roa_Db <- ModelLag1[-c(influentialRoa),]
write.csv(
  Roa_Db, 
  file = p)

```

```{r message = FALSE, error = FALSE, warning = FALSE, tidy.opts=list(blank=FALSE, width.cutoff=55),  results = 'asis', tidy = TRUE, comment = FALSE}
# I report influencial obervations on a graph

## TobinsQ
### plot cook's distance
plot(cooksdTobinsQ, 
     pch="*", 
     cex=2, 
     main = "Influential outliers - Tobin's Q")  
### add cutoff line
abline(h = 4*mean(cooksdTobinsQ, na.rm=T), col="red")
### add labels
text(x=1:length(cooksdTobinsQ)+1, y=cooksdTobinsQ, labels=ifelse(cooksdTobinsQ>4*mean(cooksdTobinsQ, na.rm=T),names(cooksdTobinsQ),""), col="red")  
```

\newpage
```{r  message = FALSE, error = FALSE, warning = FALSE, tidy.opts=list(blank=FALSE, width.cutoff=55),  results = 'asis', tidy = TRUE, comment = FALSE}
## Roa
### plot cook's distance
plot(cooksdRoa, 
     pch="*", 
     cex=2, 
     main = "Influential outliers - ROA")  
### add cutoff line
abline(h = 4*mean(cooksdRoa, na.rm=T), col="red")  
### add labels
text(x=1:length(cooksdRoa)+1, y=cooksdRoa, 
     labels=ifelse(cooksdRoa>4*mean(cooksdRoa, na.rm=T),names(cooksdRoa),""), 
     col="red") 
```
