---
output:
  pdf_document
header-includes:
- \usepackage{placeins}
- \usepackage{fancyhdr}
- \usepackage{setspace}
- \usepackage{chngcntr}
- \onehalfspacing
- \counterwithin{figure}{section}
- \counterwithin{table}{section}
- \usepackage{rotating}
- \usepackage{dcolumn}
---

```{r echo = FALSE, message = FALSE, error = FALSE, warning = FALSE, results = 'asis'}

################################################
############## Package loading #################
################################################

rm(list=ls()) #Removes all items in the R environment
if (!require("plm")) install.packages("plm")
library(plm) 
if (!require("dplyr")) install.packages("dplyr")
library(dplyr) 
if (!require("data.table")) install.packages("data.table")
library(data.table)
if (!require("stargazer")) install.packages("stargazer")
library(stargazer)
if (!require("Hmisc")) install.packages("Hmisc")
library(Hmisc)
if (!require("lattice")) install.packages("lattice")
library(lattice)
if (!require("survival")) install.packages("survival")
library(survival)
if (!require("ggplot2")) install.packages("ggplot2")
library(ggplot2)
if (!require("car")) install.packages("car")
library(car)
if (!require("ggpubr")) install.packages("ggpubr")
library(ggpubr)
if (!require("xtable")) install.packages("xtable")
library(xtable)
```

```{r echo = FALSE, message = FALSE, error = FALSE, warning = FALSE, results = 'asis'}
# Database Loading. Here I consider the database with outliers.
DataBase <- read.csv(file = "Analysis/DataBase/DataSynchronization/Lag1.csv", header = TRUE, stringsAsFactors = FALSE)

## I create a new df called "model" which contains only variables that I need

Model <- DataBase %>% select(c(YearIndex,
                               CompaniesIndex,
                               Roa,
                               TobinsQ,
                               DebtToEquityRatio,
                               NetMargin,
                               TotalAssets,
                               GicsClassification,
                               CarbonProductivity,
                               WaterProductivity,
                               WasteProductivity,
                               SustainabilityPayLink,
                               SustainableThemedCommitment,
                               AuditScore,
                               GreenScore
                               ))

## I transform the "TotalAssets" column into FirmSize using the log of TotalAssets 
Model$TotalAssets <- log10(Model$TotalAssets)

## I use the natural log for TobinsQ
Model$TobinsQ <- log10(Model$TobinsQ)

## I rename some columns

Model1 <- Model %>% setnames(old = c("Roa", "DebtToEquityRatio", "TotalAssets", "GicsClassification", "NetMargin", "CarbonProductivity", "WaterProductivity", "WasteProductivity", "SustainabilityPayLink", "SustainableThemedCommitment", "AuditScore"), new = c("ROA", "Leverage", "FirmSize", "Industry", "Growth", "CaP", "WaP", "WastP", "SPL", "STC", "AS"))

```

# Results

The `R` script of this section is available in *"[Appendix B: Results - R Script]"*.

## Descriptive Statistics

```{r echo = FALSE, message = FALSE, error = FALSE, warning = FALSE, results = 'asis'}
################################################
######## unpaired two-samples t-test ###########
################################################

Sample1 <- Model1 %>% subset( subset = !is.na(ROA)) %>% select(ROA)
Sample2 <- Model1 %>% subset( subset = !is.na(TobinsQ)) %>% select(ROA)

IdenticalAnalyses <- round(t.test(Sample1, Sample2, alternative = "two.sided", var.equal = FALSE)$p.value, digits = 4)

```

This section provides an overview of the database. \autoref{DescriptiveStatistics} presents the main descriptive statistics of each variable. The sample size of ROA (i.e. N = `r sum(!is.na(Model1$Roa))`) is superior to the sample size of Tobin's Q (i.e. N = `r sum(!is.na(Model1$TobinsQ))`). Compared to ROA, *"calculating Tobin’s Q requires a relatively high number of financial variables and is more susceptible to missing values"* [@Delmas2015]. This creates a disparity among the number of observations for each dependent variables. @Delmas2015 encountered the same issue and conducted an identical analysis to check whether this introduces a sample bias. I did the same and the *p-value* of the unpaired two-sample t-test equals `r IdenticalAnalyses` meaning that there is no significant difference between both samples.

\autoref{Matrix} contains the matrix of correlation. There are highly significant correlations between outcome-based CEP variables (i.e. CaP, WatP and, WastP) and process-based CEP variables (i.e. SPL, STC and, AS) suggesting that the model could suffer from a high degree of multicollinearity. Multicollinearity inflates the standard errors of the coefficients making some variables statistically insignificant when they should be significant [@Akinwande2015]. One common practice in the literature to detect multicollinearity is the computation of the Variance Inflation Factor (i.e. VIF) [@Salmeron2018]. VIF indicates how much the estimated variance of the \(i_{th}\) regression coefficient is increased above what it would be if \(R_i^2\) equaled zero [@Obrien2007]. \autoref{VIF} reports VIF of all variables. The maximum VIF is 2,477 meaning that there is no multicollinearity in the model [@Obrien2007].
 

```{r echo = FALSE, message = FALSE, error = FALSE, warning = FALSE, results = 'asis'}
################################################
########### Descriptive statistics #############
################################################

# I remove the column "GreenScore", "CompaniesIndex" and "YearIndex". Right now I do not need it.
Model2 <- Model1 %>% select(-c(GreenScore, YearIndex, CompaniesIndex))

# I use stargazer to create a table containing descriptive statistics for each variable

stargazer(Model2, title = "Descriptive Statistics", label = "DescriptiveStatistics", header = FALSE, type = "latex", align = FALSE, table.placement = "b", digits = 2, digits.extra = 2)

```

```{r echo = FALSE, message = FALSE, error = FALSE, warning = FALSE, results = 'asis'}
################################################
########### Matrix of correlation ##############
################################################

# The corstars function allows to create the matrix of correlation. This function contains 4 arguments: a dataframe, the method to use, the visual appearance of the matrix (i.e. if you prefer to keep the upper or lower triangle of the matrix and lasly the type of the output (i.e. "none", "html" or "latex"))

corstars <-function(x, method=c("pearson", "spearman"), removeTriangle=c("upper", "lower"), result=c("none", "html", "latex")){
  
    #Compute correlation matrix
    require(Hmisc)
    x <- as.matrix(x)
    correlation_matrix<-rcorr(x, type=method[1])
    R <- correlation_matrix$r # Matrix of correlation coeficients
    p <- correlation_matrix$P # Matrix of p-value 
    
    ## Define notions for significance levels; spacing is important.
    mystars <- ifelse(p < .01, "*** ", ifelse(p < .05, "**  ", ifelse(p < .1, "*   ", "    ")))
    
    ## trunctuate the correlation matrix to two decimal
    R <- format(round(cbind(rep(-1.11, ncol(x)), R), 2))[,-1]
    
    ## build a new matrix that includes the correlations with their apropriate stars
    Rnew <- matrix(paste(R, mystars, sep=""), ncol=ncol(x))
    diag(Rnew) <- paste(diag(R), " ", sep="")
    rownames(Rnew) <- colnames(x)
    colnames(Rnew) <- paste(colnames(x), "", sep="")
    
    ## remove upper triangle of correlation matrix
    if(removeTriangle[1]=="upper"){
      Rnew <- as.matrix(Rnew)
      Rnew[upper.tri(Rnew, diag = TRUE)] <- ""
      Rnew <- as.data.frame(Rnew)
    }
    
    ## remove lower triangle of correlation matrix
    else if(removeTriangle[1]=="lower"){
      Rnew <- as.matrix(Rnew)
      Rnew[lower.tri(Rnew, diag = TRUE)] <- ""
      Rnew <- as.data.frame(Rnew)
    }
    
    ## remove last column and return the correlation matrix
    Rnew <- cbind(Rnew[1:length(Rnew)-1])
    if (result[1]=="none") return(Rnew)
    else{
      if(result[1]=="html") print(xtable(Rnew), type="html")
      else print(xtable(Rnew), type="latex") 
    }
} 

# I use the function on my database (i.e. Model2)

CorMatrix <- corstars(Model2, method = "pearson", removeTriangle = "upper",  result = "none")

# Right now, the names of each variable stand in both the names of the row and the column. I do not need to have dupplicates. So I keep the names of the variables as names of the row and I use a number for the names of the column.

number <- c( 1 : (ncol(Model2) - 1)) #number of variables
colnames(CorMatrix) <- number
NewRowNames <- paste(c( 1 : ncol(Model2)), rownames(CorMatrix), sep = ". ")
rownames(CorMatrix) <- NewRowNames

# I use stargazer to make a nice table

table <- stargazer(CorMatrix, summary = FALSE, type = "latex", title = "Correlation Matrix" , label = "Matrix", float=TRUE, float.env = "sidewaystable", header = FALSE, table.placement = "h", column.sep.width = "2pt", font.size = "small", notes = "Note : * p<0.1; ** p<0.05; *** p<0.01", notes.align = "r", align = TRUE)

```

```{r echo = FALSE, message = FALSE, error = FALSE, warning = FALSE, results = 'asis'}
################################################
######### Variance Inflation Factor  ###########
################################################

# I make Model1 a plm database

Model1 <- pdata.frame(Model1, index = c("CompaniesIndex", "YearIndex"))


# The vif function can not be used with within model. I need to estimate my models with the pooling model.
Roa <- plm(ROA ~ SPL + STC + AS + CaP + WaP + WastP + Leverage + Growth + FirmSize + Industry, model = "pooling", data = Model1, index = c("YearIndex", "CompaniesIndex"))

TobinsQ <- plm(TobinsQ ~ SPL + STC + AS + CaP + WaP + WastP + Leverage + Growth + FirmSize + Industry, model = "pooling", data = Model1, index = c("YearIndex", "CompaniesIndex"))


#VIF Calculation and summary in a nice stargazer table

VifRoa <- car::vif(Roa)
VifTobin <- car::vif(TobinsQ)


VifTable <- cbind(VifRoa, VifTobin)
colnames(VifTable) <- c("ROA", "TobinsQ")



stargazer(VifTable, summary = FALSE, title = "Variance Inflation Factor", label = "VIF", header = FALSE, type = "latex", align = TRUE, table.placement = "!", digits = 3)
```


## Outliers Treatment

@Lyu2015 has defined outliers as observations in the dataset that appear to be unusual and discordant and which could lead to inconsistent results. @Osborne2004 showed that even a small proportion of outliers can significantly affect simple analyses (i.e. t-tests, correlations and ANOVAs). @Cousineau2010 claimed that outliers are an issue only and only if they are influential (i.e. any extreme observations whose removal causes a different conclusion in the analysis). 

How to treat influential outliers has been a lively debate in the literature [@OrrJohn1991; @Cousineau2010]. @Tabachnick2007 argued that the imputation with the mean is the best method while @Cousineau2010 highlighted that it tends to reduce the spread of the population, making the observed distribution more leptokurtic, and possibly increase the likelihood of a type-I error. @Dang2009 advocated that a more elaborate technique involves replacing outliers with possible values (e.g. multiple imputations) while @Barnett1994 stressed that the best option is to remove or winsorize them. Alternatively, @Pollet2017 argued that inclusion or exclusion of outliers depend on the significativity of the results. According to them, if results are more significant without outliers, scholars should remove them.

Following the mindset of @Pollet2017, I removed outliers from the database. Influential outliers have been identified based on the Cook's distance [@Cook1977] which is a common statistical tool to assess the influence of outliers [@JPStevens1984; @Cousineau2010; @Zuurprotocoldataexploration2010]. Cook’s Distance observes the difference between the regression parameters of a given model, \(\hat{\beta}\), and what they become if the \(i_{th}\) data point is deleted, let's say  \(\hat{\beta}_{i}\). See *"[Appendix C: Outliers Treatment]"* for further details on how I proceed.

## The Impact of Process-Based CEP on Outcome-Based CEP

\autoref{CepResults} reports the main results of the analysis of the impact of process-based CEP (i.e. SPL, STC and AS) on outcome-based CEP (i.e. CaP, WatP and WastP). Given the p-value of the F test, all models have FE making the *fixed effects estimation* the most efficient estimator.  

Except for Model (1) which indicates no significant relation between SPL and CaP, all models show evidence of a positive and highly statistically significant effect of process-based CEP on outcome-based CEP. Indeed, results demonstrate that companies, which link the remuneration of any member of a company’s senior executive team with the achievement of environmental performance targets, have a better WatP (+0.022%) and WastP (+0.025%). The fact of having a sustainability committee on the board of directors level increases the CaP (+0.058%), WatP (+0.067%) and, WastP (+0.046%). Finally, companies having their latest reported environmental metrics audited by a third party have a higher CaP (+0.057%), WatP (+0.068%) and, WastP (+0.071%). Hence, hypothesis 1 is verified.


```{r echo = FALSE, message = FALSE, error = FALSE, warning = FALSE, results = 'asis'}
################################################
######## Process vs outcome based CEP ##########
################################################

# I select only CEP variables in model2. As Model2 is already a pdata.frame, I do not need to reproduce this function on Model3.

Model3 <- Model1 %>% 
  select(c(YearIndex,
           CompaniesIndex,
           CaP, 
           WaP, 
           WastP, 
           SPL,
           STC,
           AS,
           Leverage, 
           FirmSize, 
           Industry, 
           Growth
           )) 


# I test for Random Effect Model using the Lagrange Multiplier Tests for Panel Models. 

## Pooling Model
  CarbonPooling <- plm(CaP ~ SPL + STC + AS + FirmSize + Leverage + Growth + Industry, data = Model3, model="pooling")

  WaterPooling <- plm(WaP ~ SPL + STC + AS + FirmSize + Leverage + Growth + Industry, data = Model3, model="pooling")

  WastePooling <- plm(WastP ~ SPL + STC + AS + FirmSize + Leverage + Growth + Industry, data = Model3, model="pooling")

  ## Plmtest
  PlmtestCarbon <- as.numeric(round(plmtest(CarbonPooling, effect = "time", type = "bp")$p.value, digits = 3))
  PlmtestWater <- as.numeric(round(plmtest(WaterPooling, effect = "time", type = "bp")$p.value, digits = 3))
  PlmtestWaste <- as.numeric(round(plmtest(WastePooling, effect = "time", type = "bp")$p.value, digits = 3))

  ## Improve p-value understanding
  PlmtestCarbon<-ifelse(PlmtestCarbon<0.01, paste(PlmtestCarbon,"***",sep = ""),
		ifelse(PlmtestCarbon<0.05,paste(PlmtestCarbon,"**",sep = ""),
		ifelse(PlmtestCarbon<0.1,paste(PlmtestCarbon,"*",sep = ""),PlmtestCarbon)))
  PlmtestWater<-ifelse(PlmtestWater<0.01, paste(PlmtestWater,"***",sep = ""),
		ifelse(PlmtestWater<0.05,paste(PlmtestWater,"**",sep = ""),
		ifelse(PlmtestWater<0.1,paste(PlmtestWater,"*",sep = ""),PlmtestWater)))
  PlmtestWaste<-ifelse(PlmtestWaste<0.01, paste(PlmtestWaste,"***",sep = ""),
		ifelse(PlmtestWaste<0.05,paste(PlmtestWaste,"**",sep = ""),
		ifelse(PlmtestWaste<0.1,paste(PlmtestWaste,"*",sep = ""),PlmtestWaste)))
  
  
# I test for Fixed Effect Model using pFtest which is a test of individual and/or time effects based on the comparison of the within and the pooling model.
  
  ## Within Model with time effect
  
  CarbonWithin <- plm(CaP ~ SPL + STC + AS + FirmSize + Leverage + Growth + Industry, data = Model3, model="within", effect = "time")

  WaterWithin <- plm(WaP ~ SPL + STC + AS + FirmSize + Leverage + Growth + Industry, data = Model3, model="within", effect = "time")

  WasteWithin <- plm(WastP ~ SPL + STC + AS + FirmSize + Leverage + Growth + Industry, data = Model3, model="within", effect = "time")
  
  ## pFtest
  
  pFtestCarbon <- as.numeric(round(pFtest(CarbonWithin, CarbonPooling)$p.value, digits = 3))
  
  pFtestWater <- as.numeric(round(pFtest(WaterWithin, WaterPooling)$p.value, digits = 3))
  
  pFtestWaste <- as.numeric(round(pFtest(WasteWithin, WastePooling)$p.value, digits = 3))
  
  ## Improve p-value understanding
  pFtestCarbon<-ifelse(pFtestCarbon<0.01, paste(pFtestCarbon,"***",sep = ""),
		ifelse(pFtestCarbon<0.05,paste(pFtestCarbon,"**",sep = ""),
		ifelse(pFtestCarbon<0.1,paste(pFtestCarbon,"*",sep = ""),pFtestCarbon)))
  pFtestWater<-ifelse(pFtestWater<0.01, paste(pFtestWater,"***",sep = ""),
		ifelse(pFtestWater<0.05,paste(pFtestWater,"**",sep = ""),
		ifelse(pFtestWater<0.1,paste(pFtestWater,"*",sep = ""),pFtestWater)))
  pFtestWaste<-ifelse(pFtestWaste<0.01, paste(pFtestWaste,"***",sep = ""),
		ifelse(pFtestWaste<0.05,paste(pFtestWaste,"**",sep = ""),
		ifelse(pFtestWaste<0.1,paste(pFtestWaste,"*",sep = ""),pFtestWaste)))


# Based on the results of the tests, the three models need to be estimated with the fixed effects estimations (i.e. model = "within" in plm). Let's consolidate into a stargazer table
  
stargazer(CarbonWithin, WaterWithin, WasteWithin, title = "The Impact of Process-Based on Outcome-Based CEP", label = "CepResults", header = FALSE, single.row = TRUE,  type = "latex", align = FALSE, model.numbers = FALSE, table.placement = "!", column.labels   = c("Model (1)", "Model (2)", "Model (3)"), add.lines = list(c("BPLM test (pvalue)", PlmtestCarbon, PlmtestWater, PlmtestWaste),
                           c("F test (pvalue)", pFtestCarbon ,pFtestWater, pFtestWaste)))

```

## The Impact of CEP on CFP 

\autoref{Lag1} reports the main results of the analysis of the impact of both process-based CEP (i.e. SPL, STC and AS) and outcome-based CEP (i.e. CaP, WatP and WastP) on short-term CFP (ROA) and long-term CFP (i.e. TobinsQ). Based on the pvalue of BPLM and F tests, model (4) has been estimated with the *pooled OLS estimation* while model (5) has been estimated with the *fixed effects estimation*. 

Model (4) shows evidence of a positive and statistically significant effect of SPL, AS, and WaP on *long-term CFP*. Model (5) shows evidence of a positive and statistically significant effect of SPL, STC and CaP on *short-term CFP*.

More precisely, regarding process-based CEP variables, results stress that companies, which link the remuneration of any member of a company’s senior executive team with the achievement of environmental performance targets, are characterized by both a higher Tobin's Q (+0.079) and ROA (+0.008). Then, the fact of having a sustainability committee on the board of directors level increases the ROA (+0.012). Finally, companies having their latest reported environmental metrics audited by a third party have a higher Tobin's Q (+0.158). Regarding outcome-based CEP variables, results demonstrate that a 1% increase of carbon productivity increases the ROA (+0.03) and a 1% increase of water productivity increases the Tobin's Q (+0.337). Hence, hypotheses 2, 3, 4 and 5 are verified.

Regarding control variables, firm size and industry sector negatively and significantly influence CFP in both models while growth has a positive impact, with an effect more pronounced in Model (4). These results support previous research [@EndrikatMakingsenseconflicting2014; @MiroshnychenkoGreenpracticesfinancial2017]. Against all odds, leverage does not have any significant impact.

```{r echo = FALSE, message = FALSE, error = FALSE, warning = FALSE, results = 'asis'}
################################################
######## The impact of CEP on CFP ##############
################################################

# I have already removed outliers from both model (i.e. Roa and TobinsQ) through the file = "Analysis/MakeFile_RemoveOutliers_Lag1.rmd". Consequently I just need to download them in this file.
RoaNoOut <- read.csv(file = "Analysis/DataBase/DataSynchronization/NoOutliersLag1/Roa.csv", header = TRUE, stringsAsFactors = FALSE)

TobinNoOut <- read.csv(file = "Analysis/DataBase/DataSynchronization/NoOutliersLag1/TobinsQ.csv", header = TRUE, stringsAsFactors = FALSE)

# I change names
RoaNoOut <- RoaNoOut %>% setnames(old = c("Roa", "FinancialLeverage","CarbonProductivity", "WaterProductivity", "WasteProductivity", "SustainabilityPayLink", "SustainableThemedCommitment", "AuditScore"), new = c("ROA", "Leverage", "CaP", "WaP", "WastP", "SPL", "STC", "AS"))
TobinNoOut <- TobinNoOut %>% setnames(old = c("Roa", "FinancialLeverage","CarbonProductivity", "WaterProductivity", "WasteProductivity", "SustainabilityPayLink", "SustainableThemedCommitment", "AuditScore"), new = c("ROA", "Leverage", "CaP", "WaP", "WastP", "SPL", "STC", "AS"))
 
# I make both df a plm dataframe
RoaNoOut <- RoaNoOut %>% pdata.frame(index = c("CompaniesIndex", "YearIndex"))
TobinNoOut <- TobinNoOut %>% pdata.frame(index = c("CompaniesIndex", "YearIndex"))

# I test for Random Effect Model using the Lagrange Multiplier Tests for Panel Models. 

  ## Pooling Model
  RoaPooling <- plm(ROA ~ SPL + STC + AS + CaP + WaP + WastP + FirmSize + Leverage + Growth + Industry, data = RoaNoOut, model="pooling")
  TobinPooling <- plm(TobinsQ ~ SPL + STC + AS + CaP + WaP + WastP + FirmSize + Leverage + Growth + Industry, data = TobinNoOut, model="pooling")


  ## Plmtest
  PlmtestRoa <-as.numeric(round(plmtest(RoaPooling, effect = "time", type = "bp")$p.value, digits = 3))
  PlmtestTobin <-as.numeric(round(plmtest(TobinPooling, effect = "time", type = "bp")$p.value, digits = 3))

  ## Improve p-value understanding
  PlmtestRoa<-ifelse(PlmtestRoa<0.01, paste(PlmtestRoa,"***",sep = ""),
		ifelse(PlmtestRoa<0.05,paste(PlmtestRoa,"**",sep = ""),
		ifelse(PlmtestRoa<0.1,paste(PlmtestRoa,"*",sep = ""),PlmtestRoa)))
  PlmtestTobin<-ifelse(PlmtestTobin<0.01, paste(PlmtestTobin,"***",sep = ""),
		ifelse(PlmtestTobin<0.05,paste(PlmtestTobin,"**",sep = ""),
		ifelse(PlmtestTobin<0.1,paste(PlmtestTobin,"*",sep = ""),PlmtestTobin)))
  
# I test for Fixed Effect Model using pFtest which is a test of individual and/or time effects based on the comparison of the within and the pooling model.
  
  ## Within Model with time effect
  
  RoaWithin <- plm(ROA ~ SPL + STC + AS + CaP + WaP + WastP + FirmSize + Leverage + Growth + Industry, data = RoaNoOut, model="within", effect = "time")
  TobinWithin <- plm(TobinsQ ~ SPL + STC + AS + CaP + WaP + WastP + FirmSize + Leverage + Growth + Industry, data = TobinNoOut, model = "within", effect = "time")
  
  ## pFtest
  
  pFtestRoa <- as.numeric(round(pFtest(RoaWithin, RoaPooling)$p.value, digits = 3))
  pFtestTobin <- as.numeric(round(pFtest(TobinWithin, TobinPooling)$p.value, digits = 3))

  ## Improve p-value understanding
  pFtestRoa<-ifelse(pFtestRoa<0.01, paste(pFtestRoa, "***",sep = ""),
		ifelse(pFtestRoa<0.05,paste(pFtestRoa,"**",sep = ""),
		ifelse(pFtestRoa<0.1,paste(pFtestRoa,"*",sep = ""),pFtestRoa)))
  pFtestTobin<-ifelse(pFtestTobin<0.01, paste(pFtestTobin,"***",sep = ""),
		ifelse(pFtestTobin<0.05,paste(pFtestTobin,"**",sep = ""),
		ifelse(pFtestTobin<0.1,paste(pFtestTobin,"*",sep = ""),pFtestTobin)))
  
# Based on the results of the tests, TobinsQ need to be estimated with the pooling OLS estimations (i.e. model = "pooling" in plm) while Roa with the within effect estimation.. Let's consolidate into a nice stargazer table
  
stargazer(TobinPooling, RoaWithin, title = "The Impact of Process and Outcome-Based CEP on CFP (Lag = 1)", label = "Lag1", header = FALSE, type = "latex", single.row = TRUE, align = FALSE, model.numbers = FALSE, table.placement = "!", column.labels   = c("Model (4)", "Model (5)"), add.lines = list(c("BPLM test (pvalue)", PlmtestTobin, PlmtestRoa),
                           c("F test (pvalue)", pFtestTobin ,pFtestRoa)))

```



