---
output:
  pdf_document
---



```{r echo = FALSE, message = FALSE, error = FALSE, warning = FALSE, results = 'asis'}

################################################
############## Package loading #################
################################################

rm(list=ls()) #Removes all items in the R environment
if (!require("plm")) install.packages("plm")
library(plm) 
if (!require("dplyr")) install.packages("dplyr")
library(dplyr) 
if (!require("data.table")) install.packages("data.table")
library(data.table)
if (!require("stargazer")) install.packages("stargazer")
library(stargazer)
```

# Sensitivity Analysis

To ensure the robustness of the main findings of the previous section, I carry out a Sensitivity Analysis (i.e. SA). SA investigates how the variation in the output of equation \ref{EconometricModel} can be attributed to variations of its input [@Pianosi2016]. First, equation \ref{EconometricModel} has been re-estimated using a lagged variables of two years, such as:

\begin{equation}
\centering
\begin{aligned}
Y_{it+2} & = & \alpha + \beta_{1} SPL_{it} + \beta_{2} STC_{it} + \beta_{3} AS_{it} + \beta_{4} CaP_{it} \\
&& + { }  \beta_{5} WatP_{it} + \beta_{6} WastP_{it} + Controls_{it} + d_{t} + u_{it}
\label{EconometricModelLag2}
\end{aligned}
\end{equation}


where \(Y_{it+2}\) is a proxy of CFP measured as ROA or Tobin's Q, \(SPL_{it}\) is a proxy for a firm's sustainability pay link, \(STC_{it}\) is a proxy for a firm's sustainability themed commitment, \(AS_{it}\) is a proxy for a firm's audit score, \(CP_{it}\) is a proxy for a firm's carbon productivity, \(WatP_{it}\) is a proxy for a firm's water productivity, \(WasP_{it}\) is a proxy for a firm's waste productivity, \(Controls_{it}\) is a vector of control variables that includes firm size, industry sector, financial leverage and growth, \(d_{t}\) represents the time effect and \(u_{it}\) is the error term.

Estimators of equation \ref{EconometricModelLag2} are reported in table \ref{Lag2}. Based on the results of both BPLM and F tests, estimators has been estimated with the *pooled OLS estimation*. Except for the estimator of WaP in Model (4) which loses its significativity, findings stay the same than in section: *"[Results]"*. 

Second, I use the Green Score (i.e. GS) assigned to each company of the NGR as an alternative proxy for CEP. GS is based on a weighted average of the KPI of the ranking. Concretely, it means that equation \ref{EconometricModel} becomes:

\begin{equation}
\centering
Y_{it+1} = \alpha + \beta_{1} GS_{it} + ContrOLS_{it} + d_{t} + u_{it}
\label{GreenScoreEquation}
\end{equation}


where \(Y_{it+1}\) is a proxy of CFP measured as ROA or Tobin's Q, \(GS_{it}\) is a proxy for a firm's green score, \(ContrOLS_{it}\) is a vector of control variables that includes firm size, industry sector, financial leverage and growth, \(d_{t}\) represents time effect and  \(u_{it}\) is the error term.

Given the pvalue of both BPLM and F tests, Model (4) has been estimated with the *pooled OLS estimation* while Model (5) has been estimated with the *fixed effect estimation*. Results are reported in table \ref{GreenScoreResults} and confirm findings of the section: *"[Results]"*. More precisely, it shows that a 1% increase of GS increases the long-term CFP (+0.669) and the short-term CFP (+0.051).

Hence, the SA supports that CEP does have a significant and positive effect on CFP, no matter the time horizon (short-term and long-term), and is stronger with a long-term perspective than a short-term perspective. `R` script of this section is available in *"[Appendix D: Sensitivity Analysis - R Script]"*.


\newpage
```{r echo = FALSE, message = FALSE, error = FALSE, warning = FALSE, results = 'asis'}
################################################
######## The impact of CEP on CFP ##############
################################################

# I have already removed outliers from both model (i.e. Roa and TobinsQ) through the file = "Analysis/MakeFile_RemoveOutliers_Lag1.rmd". Consequently I just need to download them in this file.
RoaNoOut <- read.csv(file = "Analysis/DataBase/DataSynchronization/NoOutliersLag2/Roa.csv", header = TRUE, stringsAsFactors = FALSE)

TobinNoOut <- read.csv(file = "Analysis/DataBase/DataSynchronization/NoOutliersLag2/TobinsQ.csv", header = TRUE, stringsAsFactors = FALSE)

# I change names
RoaNoOut <- RoaNoOut %>% setnames(old = c("Roa", "FinancialLeverage","CarbonProductivity", "WaterProductivity", "WasteProductivity", "SustainabilityPayLink", "SustainableThemedCommitment", "AuditScore"), new = c("ROA", "Leverage", "CaP", "WaP", "WastP", "SPL", "STC", "AS"))
TobinNoOut <- TobinNoOut %>% setnames(old = c("Roa", "FinancialLeverage","CarbonProductivity", "WaterProductivity", "WasteProductivity", "SustainabilityPayLink", "SustainableThemedCommitment", "AuditScore"), new = c("ROA", "Leverage", "CaP", "WaP", "WastP", "SPL", "STC", "AS"))

# I make both df a plm dataframe
RoaNoOut <- RoaNoOut %>% pdata.frame(index = c("CompaniesIndex", "YearIndex"))
TobinNoOut <- TobinNoOut %>% pdata.frame(index = c("CompaniesIndex", "YearIndex"))

# I test for Random Effect Model using the Lagrange Multiplier Tests for Panel Models. 

  ## Pooling Model
  RoaPooling <- plm(ROA ~ SPL + STC + AS + CaP + WaP + WastP + FirmSize + Leverage + Growth + Industry, data = RoaNoOut, model="pooling")
  TobinPooling <- plm(TobinsQ ~ SPL + STC + AS + CaP + WaP + WastP + FirmSize + Leverage + Growth + Industry, data = TobinNoOut, model="pooling")


  ## Plmtest
  PlmtestRoa <-as.numeric(round(plmtest(RoaPooling, effect = "time", type = "bp")$p.value, digits = 3))
  PlmtestTobin <-as.numeric(round(plmtest(TobinPooling, effect = "time", type = "bp")$p.value, digits = 3))

  ## Improve p-value understanding
  PlmtestRoa<-ifelse(PlmtestRoa<0.01, paste(PlmtestRoa,"***",sep = ""),
		ifelse(PlmtestRoa<0.05,paste(PlmtestRoa,"**",sep = ""),
		ifelse(PlmtestRoa<0.1,paste(PlmtestRoa,"*",sep = ""),PlmtestRoa)))
  PlmtestTobin<-ifelse(PlmtestTobin<0.01, paste(PlmtestTobin,"***",sep = ""),
		ifelse(PlmtestTobin<0.05,paste(PlmtestTobin,"**",sep = ""),
		ifelse(PlmtestTobin<0.1,paste(PlmtestTobin,"*",sep = ""),PlmtestTobin)))
  
# I test for Fixed Effect Model using pFtest which is a test of individual and/or time effects based on the comparison of the within and the pooling model.
  
  ## Within Model with time effect
  
  RoaWithin <- plm(ROA ~ SPL + STC + AS + CaP + WaP + WastP + FirmSize + Leverage + Growth + Industry, data = RoaNoOut, model="within", effect = "time")
  TobinWithin <- plm(TobinsQ ~ SPL + STC + AS + CaP + WaP + WastP + FirmSize + Leverage + Growth + Industry, data = TobinNoOut, model = "within", effect = "time")
  
  ## pFtest
  
  pFtestRoa <- as.numeric(round(pFtest(RoaWithin, RoaPooling)$p.value, digits = 3))
  pFtestTobin <- as.numeric(round(pFtest(TobinWithin, TobinPooling)$p.value, digits = 3))

  ## Improve p-value understanding
  pFtestRoa<-ifelse(pFtestRoa<0.01, paste(pFtestRoa, "***",sep = ""),
		ifelse(pFtestRoa<0.05,paste(pFtestRoa,"**",sep = ""),
		ifelse(pFtestRoa<0.1,paste(pFtestRoa,"*",sep = ""),pFtestRoa)))
  pFtestTobin<-ifelse(pFtestTobin<0.01, paste(pFtestTobin,"***",sep = ""),
		ifelse(pFtestTobin<0.05,paste(pFtestTobin,"**",sep = ""),
		ifelse(pFtestTobin<0.1,paste(pFtestTobin,"*",sep = ""),pFtestTobin)))
  
# Based on the results of the tests, the two models need to be estimated with the pooling OLS estimations (i.e. model = "pooling" in plm). Let's consolidate into a nice stargazer table
  
stargazer(TobinPooling, RoaPooling, title = "The Impact of Process and Outcome-Based CEP on CFP (Lag = 2)", label = "Lag2", header = FALSE, single.row = TRUE, column.labels = c("Model (4)", "Model (5)"), type = "latex", align = FALSE, model.numbers = FALSE, table.placement = "!", add.lines = list(c("BPLM test (pvalue)", PlmtestTobin, PlmtestRoa),
                           c("F test (pvalue)", pFtestTobin ,pFtestRoa)))

```


\newpage
```{r echo = FALSE, message = FALSE, error = FALSE, warning = FALSE, results = 'asis'}
################################################
###### GreenScore as an alternative ############
################################################

# I have already removed outliers from both model (i.e. Roa and TobinsQ) through the file = "Analysis/MakeFile_RemoveOutliers_Lag1.rmd". Consequently I just need to download them in this file.
RoaNoOut <- read.csv(file = "Analysis/DataBase/DataSynchronization/NoOutliersLag1/GreenScore/Roa.csv", header = TRUE, stringsAsFactors = FALSE)

TobinNoOut <- read.csv(file = "Analysis/DataBase/DataSynchronization/NoOutliersLag1/GreenScore/TobinsQ.csv", header = TRUE, stringsAsFactors = FALSE)

# I change names
RoaNoOut <- RoaNoOut %>% setnames(old = c("GreenScore", "FinancialLeverage", "Roa"), new = c("GS", "Leverage", "ROA"))
TobinNoOut <- TobinNoOut %>% setnames(old = c("GreenScore", "FinancialLeverage", "Roa"), new = c("GS", "Leverage", "ROA"))


# I make both df a plm dataframe
RoaNoOut <- RoaNoOut %>% pdata.frame(index = c("CompaniesIndex", "YearIndex"))
TobinNoOut <- TobinNoOut %>% pdata.frame(index = c("CompaniesIndex", "YearIndex"))

# I test for Random Effect Model using the Lagrange Multiplier Tests for Panel Models. 

  ## Pooling Model
  RoaPooling <- plm(ROA ~ GS + FirmSize + Leverage + Growth + Industry, data = RoaNoOut, model="pooling")
  TobinPooling <- plm(TobinsQ ~ GS + FirmSize + Leverage + Growth + Industry, data = TobinNoOut, model="pooling")


  ## Plmtest
  PlmtestRoa <- as.numeric(round(plmtest(RoaPooling, effect = "time", type = "bp")$p.value, digits = 3))
  PlmtestTobin <- as.numeric(round(plmtest(TobinPooling, effect = "time", type = "bp")$p.value, digits = 3))

  ## Improve p-value understanding
  PlmtestRoa<-ifelse(PlmtestRoa<0.01, paste(PlmtestRoa,"***",sep = ""),
		ifelse(PlmtestRoa<0.05,paste(PlmtestRoa,"**",sep = ""),
		ifelse(PlmtestRoa<0.1,paste(PlmtestRoa,"*",sep = ""), PlmtestRoa)))
  PlmtestTobin<-ifelse(PlmtestTobin<0.01, paste(PlmtestTobin,"***",sep = ""),
		ifelse(PlmtestTobin<0.05,paste(PlmtestTobin,"**",sep = ""),
		ifelse(PlmtestTobin<0.1,paste(PlmtestTobin,"*",sep = ""),PlmtestTobin)))
  
# I test for Fixed Effect Model using pFtest which is a test of individual and/or time effects based on the comparison of the within and the pooling model.
  
  ## Within Model with time effect
  
  RoaWithin <- plm(ROA ~ GS + FirmSize + Leverage + Growth + Industry, data = RoaNoOut, model = "within", effect = "time")
  TobinWithin <- plm(TobinsQ ~ GS + FirmSize + Leverage + Growth + Industry, data = TobinNoOut, model = "within", effect = "time")
  
  ## pFtest
  
  pFtestRoa <- as.numeric(round(pFtest(RoaWithin, RoaPooling)$p.value, digits = 3))
  
  pFtestTobin <- as.numeric(round(pFtest(TobinWithin, TobinPooling)$p.value, digits = 3))
  
  ## Improve p-value understanding
  pFtestRoa<-ifelse(pFtestRoa<0.01, paste(pFtestRoa,"***",sep = ""),
		ifelse(pFtestRoa<0.05,paste(pFtestRoa,"**",sep = ""),
		ifelse(pFtestRoa<0.1,paste(pFtestRoa,"*",sep = ""),pFtestRoa)))
  pFtestTobin<-ifelse(pFtestTobin<0.01, paste(pFtestTobin,"***",sep = ""),
		ifelse(pFtestTobin<0.05,paste(pFtestTobin,"**",sep = ""),
		ifelse(pFtestTobin<0.1,paste(pFtestTobin,"*",sep = ""),pFtestTobin)))

# Let's consolidate into a stargazer table
  
stargazer(TobinPooling, RoaWithin, title = "Green Score - an Alternative Variable for CEP", label = "GreenScoreResults", header = FALSE, type = "latex", align = FALSE, single.row = TRUE, model.numbers = FALSE, table.placement = "!", column.labels = c("Model (4)", "Model (5)"), add.lines = list(c("BPLM test (pvalue)", PlmtestTobin, PlmtestRoa),
                           c("F test (pvalue)", pFtestTobin ,pFtestRoa)))


```

