---
title: "Towards Green Companies: A Panel Data Study of The Environmental and Financial Performance Nexus"
#subtitle: "Master's Thesis Defence"
author: 
  - Pierrick KINIF
institute: 
  - Supervised by Sophie BÉREAU and Jean-Yves GNABO
  - University of Namur
  - Faculty of Economics, Social Sciences and Business Administration
date: June 20, 2018
output: 
  beamer_presentation:
    #incremental: true
    theme: "Darmstadt" #see http://deic.uab.es/~iblanes/beamer_gallery/index_by_theme.html
    colortheme: "beaver"
    fonttheme: "structurebold"
    toc: true
    slide_level: 2
    fig_width: 5
    fig_height: 4
    fig_caption: yes
    highlight: tango
bibliography: References.bib
csl: CSL/elsevier-harvard.csl
nocite: | 
 @PieterTans2018, @USEPA2016, @GistempTeam2018, @ImbieTeam2018
link-citations: yes
header-includes:
- \usepackage{caption}
- \usepackage{graphicx}
---

# Introduction

## Global Warming Is Not a Myth and Is Growing Fast 

\begin{figure}[h]
    \centering
    \caption{Global Atmospheric Concentrations of Carbon Dioxide Over Time}
    \includegraphics[width=0.9\textwidth, height=0.9\textheight,keepaspectratio]{figures/BeamerPresentation/PpmEvolution.png}
    \caption*{\scriptsize\textbf{Source}: Data coming from US EPA (2016) and Pieter Tans et al. (2018)}
\end{figure}

## Global Warming Is Not a Myth and Is Growing Fast 

\begin{figure}[h]
    \centering
    \caption{Global Mean Estimates Based On Land and Ocean Data}
    \includegraphics[width=0.9\textwidth, height=0.9\textheight,keepaspectratio]{figures/BeamerPresentation/TemperatureAnomaly.png}
    \caption*{\scriptsize\textbf{Source}: Data coming from Gistemp Team (2018)}
\end{figure}

## Global Warming Is Not a Myth and Is Growing Fast 

\begin{figure}[h]
    \centering
    \caption{Cumulative Antarctic Ice Sheet Mass Change}
    \includegraphics[width=0.9\textwidth, height=0.9\textheight,keepaspectratio]{figures/BeamerPresentation/AntarticMelting1992-2017.jpg}
    \caption*{\scriptsize\textbf{Source}: IMBIE team (2018)}
\end{figure}

## Global Warming Represents a Threat for Companies

- Resource depletion, effect on geography, increase of incertainty, increase of natural  disasters,...

- "The ice sheets of Antarctica hold enough water to raise global sea level by 58 meters" [@Fretwell2013]

- The @BusinessandSustainableDevelopmentCommission2017 (p12) report states: 

> *"... businesses need to pursue social and environmental sustainability as avidly as they pursue market share and shareholder value... If they don’t, the costs and uncertainty of unsustainable development could swell until there is no viable world in which to do business."*

## Turn the Threat into an Opportunity


- Companies are important stakeholders of Global Warming. 

- They are part of the **problem** but can be part of the **solution**

- The solution is **profitable**

\vfill

### Contribution of this thesis

This thesis **provides incentives** for companies to invest in environmental strategies and shows that **it does pay to be green**. Companies with better corporate environmental performance have better financal performance and the relation increases with a long-term perspective.

----

# Theoretical Framework

## Corporate Financial Performance (i.e. CFP)

### Focus on two of the three-group classification of @Orlitzky2003:

1. **Market-based measures** (e.g. price-earning ratio or Tobin's Q) consider that returns should be measured from the perspective of shareholders [@Cochran1984a]. They are considered as proxies for **long-term CFP** [@EndrikatMakingsenseconflicting2014].

2. **Accounting-based measures** require profitability and asset utilization indicators such as Return on Asset (i.e. ROA) or Return on Equity (i.e. ROE) [@Cochran1984a; @Wu2006]. They are considered as proxies for **short-term CFP** [@EndrikatMakingsenseconflicting2014].

## Corporate Environmental Performance (i.e. CEP)

### Two-group classification of @EndrikatMakingsenseconflicting2014:

1. **Process-based CEP** which refers to "a strategic level and focuses on managerial principles and processes such as environmental objectives, environmental policies, or environmental management structures". 

2. **Outcome-based CEP** which reflects "the observable and quantifiable results of these efforts [@Delmas2011a] and refers to measures such as the number of released pollutants or the ratio of recycled waste to total waste". 

## Corporate Environmental And Financial Performance Nexus

\begin{figure}[h]
\centering
\caption{Research Framework}
\includegraphics[width=0.9\textwidth, height=0.9\textheight,keepaspectratio]{figures/ResearchFramework.jpg}
\label{ResearchFramework}
\end{figure}

## Hypotheses

- **Hypothesis 1.** Process-based CEP has a positive impact on Outcome-based CEP

- **Hypothesis 2.** Outcome-based CEP has a positive impact on short-term CFP

- **Hypothesis 3.** Outcome-based CEP has a positive impact on long-term CFP

- **Hypothesis 4.** Process-based CEP has a positive impact on short-term CFP

- **Hypothesis 5.** Process-based CEP has a positive impact on long-term CFP

----

# Methodology

## Econometric Model

\scriptsize

### The link between Process-Based CEP and Outcome-Based CEP

\begin{equation}
\centering
Y_{it} = \alpha + \beta_{1} SPL_{it} + \beta_{2} STC_{it} + \beta_{3} AS_{it} + Controls_{it} + d_{t} + u_{it}
\label{CEP}
\end{equation}

\scriptsize where \(Y_{it}\) is a proxy of outcome-based CEP measured as carbon productivity, water productivity and waste productivity, \(SPL_{it}\) is a proxy for a firm's sustainability pay link, \(STC_{it}\) is a proxy for a firm's sustainability themed commitment, \(AS_{it}\) is a proxy for a firm's audit score, \(Controls_{it}\) is a vector of control variables that includes firm size, industry sector, financial leverage and growth, \(d_{t}\) represents the time effect and \(u_{it}\) is the error term.

### The link between CEP and CFP

\begin{equation}
\centering
\begin{aligned}
Y_{it+1} & = & \alpha + \beta_{1} SPL_{it} + \beta_{2} STC_{it} + \beta_{3} AS_{it} + \beta_{4} CaP_{it} \\
&& + { }  \beta_{5} WatP_{it} + \beta_{6} WastP_{it} + Controls_{it} + d_{t} + u_{it}
\label{EconometricModel}
\end{aligned}
\end{equation}

\scriptsize where \(Y_{it+1}\) is a proxy of CFP measured as ROA or Tobin's Q, \(SPL_{it}\) is a proxy for a firm's sustainability pay link, \(STC_{it}\) is a proxy for a firm's sustainability themed commitment, \(AS_{it}\) is a proxy for a firm's audit score, \(CP_{it}\) is a proxy for a firm's carbon productivity, \(WatP_{it}\) is a proxy for a firm's water productivity, \(WasP_{it}\) is a proxy for a firm's waste productivity, \(Controls_{it}\) is a vector of control variables that includes firm size, industry sector, financial leverage and growth, \(d_{t}\) represents the time effect and \(u_{it}\) is the error term.

## Panel Data

\scriptsize

### General form:

\scriptsize

\begin{equation}
\centering
Y_{it} = \alpha + \beta_k X_{itk} + u_{it} 
\label{PanelData}
\end{equation}

- with \(u_{it} = \mu_{i} + \epsilon_{it}\) 

- \(\mu_{i}\) is the individual error component and is time-invariant. It can be considered as the unobserved effect model

- \(\epsilon_{it}\), is the idiosyncratic error which is assumed well-behaved and independent of \(X_{it}\) and \(\mu_{i}\)

If \(\rho(X_{itk},\mu_{i}) \neq 0\) then \(\mu_{i}\) is considered as the *Fixed Effect* (i.e. FE) and equation \ref{PanelData} becomes:

\begin{equation}
\centering
Y_{it} = (\alpha + \mu{i}) + \beta_k X_{itk} + \epsilon_{it} 
\label{Fixed}
\end{equation}

else, \(\mu_{i}\) is considered as the *Fixed Effect* (i.e. FE) and equation \ref{PanelData} becomes:

\begin{equation}
\centering
Y_{it} = \alpha + \beta_k X_{itk} + (\epsilon_{it} + \mu{i})
\label{Random}
\end{equation}

- FE and RE models imply that OLS estimators of \(\beta_k\) are inconsistent

## Panel Data 

\scriptsize

### Testing for RE
\scriptsize

- Breusch-Pagan Lagrange Multiplier (i.e. BPLM) test [@Breusch1980]

- Examines if time and/or individual specific variance components equal zero [@Park2011]. 

- If H0 is verified, there is no RE in the panel data.

### Testing for FE
\scriptsize

- The presence of FE is tested by an F test (i.e. the function `pFtest` in `R`). 

- It tests the individual and/or time effects based on the comparison of the within and the pooling model [@Croissant2008]. 

- If H0 is verified, there is no FE in the panel data.

## Panel Data

\begin{figure}[h]
\centering
\begin{minipage}[c]{0.67\textwidth}
\includegraphics[width=\textwidth, height=\textheight,keepaspectratio]{figures/BeamerPresentation/PanelData3.png}
\end{minipage}\hfill
\begin{minipage}[c]{0.3\textwidth}
    \caption{Process to Determine the Estimation Method} 
  \end{minipage}
\end{figure}

## Endogeneity Concern

\scriptsize

### Omission variable bias

\scriptsize

Inclusion of a vector of control variables \(Controls_{it}\) that explains the relation between CEP and CFP

### Simultaneity bias

\scriptsize

There is a bidirectional causality between CEP and CFP [@EndrikatMakingsenseconflicting2014] that could cause  simultaneous causality. I used a lagged instrument \(Y_{it+1}\) to increase the confidence of the direction of the relationship [@MiroshnychenkoGreenpracticesfinancial2017]

### Presence of FE in the model

\scriptsize

Under FE, endogeneity is a concern. The Fixed Effect Estimation (i.e. equation \ref{FixedEffectsEstimation}) solves this as \(( \mu_{i} - \frac{1}{T} \displaystyle\sum_{t=1}^{T} \mu_{i} ) = 0\) [@Roberts2013].

\begin{equation}
\centering
( Y_{it} - \frac{1}{T} \displaystyle\sum_{t=1}^{T} Y_{it} ) = \beta_k (X_{itk} - \frac{1}{T} \displaystyle\sum_{t=1}^{T} X_{itk} ) + ( \epsilon_{it} - \frac{1}{T} \displaystyle\sum_{t=1}^{T} \epsilon_{it} )
\label{FixedEffectsEstimation}
\end{equation}

----

# Results

```{r echo = FALSE, message = FALSE, error = FALSE, warning = FALSE, results = 'asis'}

################################################
############## Package loading #################
################################################

#rm(list=ls()) #Removes all items in the R environment
if (!require("plm")) install.packages("plm")
library(plm) 
if (!require("dplyr")) install.packages("dplyr")
library(dplyr) 
if (!require("data.table")) install.packages("data.table")
library(data.table)
if (!require("stargazer")) install.packages("stargazer")
library(stargazer)
if (!require("Hmisc")) install.packages("Hmisc")
library(Hmisc)
if (!require("lattice")) install.packages("lattice")
library(lattice)
if (!require("survival")) install.packages("survival")
library(survival)
if (!require("ggplot2")) install.packages("ggplot2")
library(ggplot2)
if (!require("car")) install.packages("car")
library(car)
if (!require("ggpubr")) install.packages("ggpubr")
library(ggpubr)
if (!require("xtable")) install.packages("xtable")
library(xtable)
```

```{r echo = FALSE, message = FALSE, error = FALSE, warning = FALSE, results = 'asis'}
# Database Loading. Here I consider the database with outliers.
DataBase <- read.csv(file = "Analysis/DataBase/DataSynchronization/Lag1.csv", header = TRUE, stringsAsFactors = FALSE)

## I create a new df called "model" which contains only variables that I need

Model <- DataBase %>% select(c(YearIndex,
                               CompaniesIndex,
                               Roa,
                               TobinsQ,
                               DebtToEquityRatio,
                               NetMargin,
                               TotalAssets,
                               GicsClassification,
                               CarbonProductivity,
                               WaterProductivity,
                               WasteProductivity,
                               SustainabilityPayLink,
                               SustainableThemedCommitment,
                               AuditScore,
                               GreenScore
                               ))

## I transform the "TotalAssets" column into FirmSize using the log of TotalAssets 
Model$TotalAssets <- log10(Model$TotalAssets)

## I use the natural log for TobinsQ
Model$TobinsQ <- log10(Model$TobinsQ)

## I rename some columns

Model1 <- Model %>% setnames(old = c("Roa", "DebtToEquityRatio", "TotalAssets", "GicsClassification", "NetMargin", "CarbonProductivity", "WaterProductivity", "WasteProductivity", "SustainabilityPayLink", "SustainableThemedCommitment", "AuditScore"), new = c("ROA", "Leverage", "FirmSize", "Industry", "Growth", "CaP", "WaP", "WastP", "SPL", "STC", "AS"))

```

## Process-Based CEP Positively Influences Outcome-Based CEP

```{r echo = FALSE, message = FALSE, error = FALSE, warning = FALSE, results = 'asis'}
################################################
######## Process vs outcome based CEP ##########
################################################
Model1 <- pdata.frame(Model1, index = c("CompaniesIndex", "YearIndex"))
# I select only CEP variables in model2. As Model2 is already a pdata.frame, I do not need to reproduce this function on Model3.

Model3 <- Model1 %>% 
  select(c(YearIndex,
           CompaniesIndex,
           CaP, 
           WaP, 
           WastP, 
           SPL,
           STC,
           AS,
           Leverage, 
           FirmSize, 
           Industry, 
           Growth
           )) 


# I test for Random Effect Model using the Lagrange Multiplier Tests for Panel Models. 

## Pooling Model
  CarbonPooling <- plm(CaP ~ SPL + STC + AS + FirmSize + Leverage + Growth + Industry, data = Model3, model="pooling")

  WaterPooling <- plm(WaP ~ SPL + STC + AS + FirmSize + Leverage + Growth + Industry, data = Model3, model="pooling")

  WastePooling <- plm(WastP ~ SPL + STC + AS + FirmSize + Leverage + Growth + Industry, data = Model3, model="pooling")

  ## Plmtest
  PlmtestCarbon <- as.numeric(round(plmtest(CarbonPooling, effect = "time", type = "bp")$p.value, digits = 3))
  PlmtestWater <- as.numeric(round(plmtest(WaterPooling, effect = "time", type = "bp")$p.value, digits = 3))
  PlmtestWaste <- as.numeric(round(plmtest(WastePooling, effect = "time", type = "bp")$p.value, digits = 3))

  ## Improve p-value understanding
  PlmtestCarbon<-ifelse(PlmtestCarbon<0.01, paste(PlmtestCarbon,"***",sep = ""),
		ifelse(PlmtestCarbon<0.05,paste(PlmtestCarbon,"**",sep = ""),
		ifelse(PlmtestCarbon<0.1,paste(PlmtestCarbon,"*",sep = ""),PlmtestCarbon)))
  PlmtestWater<-ifelse(PlmtestWater<0.01, paste(PlmtestWater,"***",sep = ""),
		ifelse(PlmtestWater<0.05,paste(PlmtestWater,"**",sep = ""),
		ifelse(PlmtestWater<0.1,paste(PlmtestWater,"*",sep = ""),PlmtestWater)))
  PlmtestWaste<-ifelse(PlmtestWaste<0.01, paste(PlmtestWaste,"***",sep = ""),
		ifelse(PlmtestWaste<0.05,paste(PlmtestWaste,"**",sep = ""),
		ifelse(PlmtestWaste<0.1,paste(PlmtestWaste,"*",sep = ""),PlmtestWaste)))
  
  
# I test for Fixed Effect Model using pFtest which is a test of individual and/or time effects based on the comparison of the within and the pooling model.
  
  ## Within Model with time effect
  
  CarbonWithin <- plm(CaP ~ SPL + STC + AS + FirmSize + Leverage + Growth + Industry, data = Model3, model="within", effect = "time")

  WaterWithin <- plm(WaP ~ SPL + STC + AS + FirmSize + Leverage + Growth + Industry, data = Model3, model="within", effect = "time")

  WasteWithin <- plm(WastP ~ SPL + STC + AS + FirmSize + Leverage + Growth + Industry, data = Model3, model="within", effect = "time")
  
  ## pFtest
  
  pFtestCarbon <- as.numeric(round(pFtest(CarbonWithin, CarbonPooling)$p.value, digits = 3))
  
  pFtestWater <- as.numeric(round(pFtest(WaterWithin, WaterPooling)$p.value, digits = 3))
  
  pFtestWaste <- as.numeric(round(pFtest(WasteWithin, WastePooling)$p.value, digits = 3))
  
  ## Improve p-value understanding
  pFtestCarbon<-ifelse(pFtestCarbon<0.01, paste(pFtestCarbon,"***",sep = ""),
		ifelse(pFtestCarbon<0.05,paste(pFtestCarbon,"**",sep = ""),
		ifelse(pFtestCarbon<0.1,paste(pFtestCarbon,"*",sep = ""),pFtestCarbon)))
  pFtestWater<-ifelse(pFtestWater<0.01, paste(pFtestWater,"***",sep = ""),
		ifelse(pFtestWater<0.05,paste(pFtestWater,"**",sep = ""),
		ifelse(pFtestWater<0.1,paste(pFtestWater,"*",sep = ""),pFtestWater)))
  pFtestWaste<-ifelse(pFtestWaste<0.01, paste(pFtestWaste,"***",sep = ""),
		ifelse(pFtestWaste<0.05,paste(pFtestWaste,"**",sep = ""),
		ifelse(pFtestWaste<0.1,paste(pFtestWaste,"*",sep = ""),pFtestWaste)))


# Based on the results of the tests, the three models need to be estimated with the fixed effects estimations (i.e. model = "within" in plm). Let's consolidate into a stargazer table
  
stargazer(CarbonWithin, WaterWithin, WasteWithin, title = "The Impact of Process-Based on Outcome-Based CEP", label = "CepResults", header = FALSE, single.row = TRUE,  type = "latex", font.size = "tiny", omit.stat = "rsq", align = FALSE, model.numbers = FALSE, table.placement = "!", column.labels   = c("Model (1)", "Model (2)", "Model (3)"), add.lines = list(c("BPLM test (pvalue)", PlmtestCarbon, PlmtestWater, PlmtestWaste), c("F test (pvalue)", pFtestCarbon ,pFtestWater, pFtestWaste)))

```

## Both Process and Outcome-Based CEP Have a Positive Impact on CFP

```{r echo = FALSE, message = FALSE, error = FALSE, warning = FALSE, results = 'asis'}
################################################
######## The impact of CEP on CFP ##############
################################################

# I have already removed outliers from both model (i.e. Roa and TobinsQ) through the file = "Analysis/MakeFile_RemoveOutliers_Lag1.rmd". Consequently I just need to download them in this file.
RoaNoOut <- read.csv(file = "Analysis/DataBase/DataSynchronization/NoOutliersLag1/Roa.csv", header = TRUE, stringsAsFactors = FALSE)

TobinNoOut <- read.csv(file = "Analysis/DataBase/DataSynchronization/NoOutliersLag1/TobinsQ.csv", header = TRUE, stringsAsFactors = FALSE)

# I change names
RoaNoOut <- RoaNoOut %>% setnames(old = c("Roa", "FinancialLeverage","CarbonProductivity", "WaterProductivity", "WasteProductivity", "SustainabilityPayLink", "SustainableThemedCommitment", "AuditScore"), new = c("ROA", "Leverage", "CaP", "WaP", "WastP", "SPL", "STC", "AS"))
TobinNoOut <- TobinNoOut %>% setnames(old = c("Roa", "FinancialLeverage","CarbonProductivity", "WaterProductivity", "WasteProductivity", "SustainabilityPayLink", "SustainableThemedCommitment", "AuditScore"), new = c("ROA", "Leverage", "CaP", "WaP", "WastP", "SPL", "STC", "AS"))
 
# I make both df a plm dataframe
RoaNoOut <- RoaNoOut %>% pdata.frame(index = c("CompaniesIndex", "YearIndex"))
TobinNoOut <- TobinNoOut %>% pdata.frame(index = c("CompaniesIndex", "YearIndex"))

# I test for Random Effect Model using the Lagrange Multiplier Tests for Panel Models. 

  ## Pooling Model
  RoaPooling <- plm(ROA ~ SPL + STC + AS + CaP + WaP + WastP + FirmSize + Leverage + Growth + Industry, data = RoaNoOut, model="pooling")
  TobinPooling <- plm(TobinsQ ~ SPL + STC + AS + CaP + WaP + WastP + FirmSize + Leverage + Growth + Industry, data = TobinNoOut, model="pooling")


  ## Plmtest
  PlmtestRoa <-as.numeric(round(plmtest(RoaPooling, effect = "time", type = "bp")$p.value, digits = 3))
  PlmtestTobin <-as.numeric(round(plmtest(TobinPooling, effect = "time", type = "bp")$p.value, digits = 3))

  ## Improve p-value understanding
  PlmtestRoa<-ifelse(PlmtestRoa<0.01, paste(PlmtestRoa,"***",sep = ""),
		ifelse(PlmtestRoa<0.05,paste(PlmtestRoa,"**",sep = ""),
		ifelse(PlmtestRoa<0.1,paste(PlmtestRoa,"*",sep = ""),PlmtestRoa)))
  PlmtestTobin<-ifelse(PlmtestTobin<0.01, paste(PlmtestTobin,"***",sep = ""),
		ifelse(PlmtestTobin<0.05,paste(PlmtestTobin,"**",sep = ""),
		ifelse(PlmtestTobin<0.1,paste(PlmtestTobin,"*",sep = ""),PlmtestTobin)))
  
# I test for Fixed Effect Model using pFtest which is a test of individual and/or time effects based on the comparison of the within and the pooling model.
  
  ## Within Model with time effect
  
  RoaWithin <- plm(ROA ~ SPL + STC + AS + CaP + WaP + WastP + FirmSize + Leverage + Growth + Industry, data = RoaNoOut, model="within", effect = "time")
  TobinWithin <- plm(TobinsQ ~ SPL + STC + AS + CaP + WaP + WastP + FirmSize + Leverage + Growth + Industry, data = TobinNoOut, model = "within", effect = "time")
  
  ## pFtest
  
  pFtestRoa <- as.numeric(round(pFtest(RoaWithin, RoaPooling)$p.value, digits = 3))
  pFtestTobin <- as.numeric(round(pFtest(TobinWithin, TobinPooling)$p.value, digits = 3))

  ## Improve p-value understanding
  pFtestRoa<-ifelse(pFtestRoa<0.01, paste(pFtestRoa, "***",sep = ""),
		ifelse(pFtestRoa<0.05,paste(pFtestRoa,"**",sep = ""),
		ifelse(pFtestRoa<0.1,paste(pFtestRoa,"*",sep = ""),pFtestRoa)))
  pFtestTobin<-ifelse(pFtestTobin<0.01, paste(pFtestTobin,"***",sep = ""),
		ifelse(pFtestTobin<0.05,paste(pFtestTobin,"**",sep = ""),
		ifelse(pFtestTobin<0.1,paste(pFtestTobin,"*",sep = ""),pFtestTobin)))
  
# Based on the results of the tests, TobinsQ need to be estimated with the pooling OLS estimations (i.e. model = "pooling" in plm) while Roa with the within effect estimation.. Let's consolidate into a nice stargazer table
  
stargazer(TobinPooling, RoaWithin, title= "The Impact of Process and Outcome-Based CEP on CFP", label = "Lag1", header = FALSE, type = "latex", single.row = TRUE, align = FALSE, font.size = "tiny", omit.stat = "rsq", model.numbers = FALSE, table.placement = "!", column.labels   = c("Model (4)", "Model (5)"), add.lines = list(c("BPLM test (pvalue)", PlmtestTobin, PlmtestRoa),
                           c("F test (pvalue)", pFtestTobin ,pFtestRoa)))

```

----

# Sensitivity Analyses 

## Lagged Instrument of 2 Years

```{r echo = FALSE, message = FALSE, error = FALSE, warning = FALSE, results = 'asis'}
################################################
######## The impact of CEP on CFP ##############
################################################

# I have already removed outliers from both model (i.e. Roa and TobinsQ) through the file = "Analysis/MakeFile_RemoveOutliers_Lag1.rmd". Consequently I just need to download them in this file.
RoaNoOut <- read.csv(file = "Analysis/DataBase/DataSynchronization/NoOutliersLag2/Roa.csv", header = TRUE, stringsAsFactors = FALSE)

TobinNoOut <- read.csv(file = "Analysis/DataBase/DataSynchronization/NoOutliersLag2/TobinsQ.csv", header = TRUE, stringsAsFactors = FALSE)

# I change names
RoaNoOut <- RoaNoOut %>% setnames(old = c("Roa", "FinancialLeverage","CarbonProductivity", "WaterProductivity", "WasteProductivity", "SustainabilityPayLink", "SustainableThemedCommitment", "AuditScore"), new = c("ROA", "Leverage", "CaP", "WaP", "WastP", "SPL", "STC", "AS"))
TobinNoOut <- TobinNoOut %>% setnames(old = c("Roa", "FinancialLeverage","CarbonProductivity", "WaterProductivity", "WasteProductivity", "SustainabilityPayLink", "SustainableThemedCommitment", "AuditScore"), new = c("ROA", "Leverage", "CaP", "WaP", "WastP", "SPL", "STC", "AS"))

# I make both df a plm dataframe
RoaNoOut <- RoaNoOut %>% pdata.frame(index = c("CompaniesIndex", "YearIndex"))
TobinNoOut <- TobinNoOut %>% pdata.frame(index = c("CompaniesIndex", "YearIndex"))

# I test for Random Effect Model using the Lagrange Multiplier Tests for Panel Models. 

  ## Pooling Model
  RoaPooling <- plm(ROA ~ SPL + STC + AS + CaP + WaP + WastP + FirmSize + Leverage + Growth + Industry, data = RoaNoOut, model="pooling")
  TobinPooling <- plm(TobinsQ ~ SPL + STC + AS + CaP + WaP + WastP + FirmSize + Leverage + Growth + Industry, data = TobinNoOut, model="pooling")


  ## Plmtest
  PlmtestRoa <-as.numeric(round(plmtest(RoaPooling, effect = "time", type = "bp")$p.value, digits = 3))
  PlmtestTobin <-as.numeric(round(plmtest(TobinPooling, effect = "time", type = "bp")$p.value, digits = 3))

  ## Improve p-value understanding
  PlmtestRoa<-ifelse(PlmtestRoa<0.01, paste(PlmtestRoa,"***",sep = ""),
		ifelse(PlmtestRoa<0.05,paste(PlmtestRoa,"**",sep = ""),
		ifelse(PlmtestRoa<0.1,paste(PlmtestRoa,"*",sep = ""),PlmtestRoa)))
  PlmtestTobin<-ifelse(PlmtestTobin<0.01, paste(PlmtestTobin,"***",sep = ""),
		ifelse(PlmtestTobin<0.05,paste(PlmtestTobin,"**",sep = ""),
		ifelse(PlmtestTobin<0.1,paste(PlmtestTobin,"*",sep = ""),PlmtestTobin)))
  
# I test for Fixed Effect Model using pFtest which is a test of individual and/or time effects based on the comparison of the within and the pooling model.
  
  ## Within Model with time effect
  
  RoaWithin <- plm(ROA ~ SPL + STC + AS + CaP + WaP + WastP + FirmSize + Leverage + Growth + Industry, data = RoaNoOut, model="within", effect = "time")
  TobinWithin <- plm(TobinsQ ~ SPL + STC + AS + CaP + WaP + WastP + FirmSize + Leverage + Growth + Industry, data = TobinNoOut, model = "within", effect = "time")
  
  ## pFtest
  
  pFtestRoa <- as.numeric(round(pFtest(RoaWithin, RoaPooling)$p.value, digits = 3))
  pFtestTobin <- as.numeric(round(pFtest(TobinWithin, TobinPooling)$p.value, digits = 3))

  ## Improve p-value understanding
  pFtestRoa<-ifelse(pFtestRoa<0.01, paste(pFtestRoa, "***",sep = ""),
		ifelse(pFtestRoa<0.05,paste(pFtestRoa,"**",sep = ""),
		ifelse(pFtestRoa<0.1,paste(pFtestRoa,"*",sep = ""),pFtestRoa)))
  pFtestTobin<-ifelse(pFtestTobin<0.01, paste(pFtestTobin,"***",sep = ""),
		ifelse(pFtestTobin<0.05,paste(pFtestTobin,"**",sep = ""),
		ifelse(pFtestTobin<0.1,paste(pFtestTobin,"*",sep = ""),pFtestTobin)))
  
# Based on the results of the tests, the two models need to be estimated with the pooling OLS estimations (i.e. model = "pooling" in plm). Let's consolidate into a nice stargazer table
  
stargazer(TobinPooling, RoaPooling, title = "The Impact of Process and Outcome-Based CEP on CFP", label = "Lag2", header = FALSE, single.row = TRUE, font.size = "tiny", omit.stat = "rsq", column.labels = c("Model (4)", "Model (5)"), type = "latex", align = FALSE, model.numbers = FALSE, table.placement = "!", add.lines = list(c("BPLM test (pvalue)", PlmtestTobin, PlmtestRoa),
                           c("F test (pvalue)", pFtestTobin ,pFtestRoa)))

```

## Green Score as an Alternative

```{r echo = FALSE, message = FALSE, error = FALSE, warning = FALSE, results = 'asis'}
################################################
###### GreenScore as an alternative ############
################################################

# I have already removed outliers from both model (i.e. Roa and TobinsQ) through the file = "Analysis/MakeFile_RemoveOutliers_Lag1.rmd". Consequently I just need to download them in this file.
RoaNoOut <- read.csv(file = "Analysis/DataBase/DataSynchronization/NoOutliersLag1/GreenScore/Roa.csv", header = TRUE, stringsAsFactors = FALSE)

TobinNoOut <- read.csv(file = "Analysis/DataBase/DataSynchronization/NoOutliersLag1/GreenScore/TobinsQ.csv", header = TRUE, stringsAsFactors = FALSE)

# I change names
RoaNoOut <- RoaNoOut %>% setnames(old = c("GreenScore", "FinancialLeverage", "Roa"), new = c("GS", "Leverage", "ROA"))
TobinNoOut <- TobinNoOut %>% setnames(old = c("GreenScore", "FinancialLeverage", "Roa"), new = c("GS", "Leverage", "ROA"))


# I make both df a plm dataframe
RoaNoOut <- RoaNoOut %>% pdata.frame(index = c("CompaniesIndex", "YearIndex"))
TobinNoOut <- TobinNoOut %>% pdata.frame(index = c("CompaniesIndex", "YearIndex"))

# I test for Random Effect Model using the Lagrange Multiplier Tests for Panel Models. 

  ## Pooling Model
  RoaPooling <- plm(ROA ~ GS + FirmSize + Leverage + Growth + Industry, data = RoaNoOut, model="pooling")
  TobinPooling <- plm(TobinsQ ~ GS + FirmSize + Leverage + Growth + Industry, data = TobinNoOut, model="pooling")


  ## Plmtest
  PlmtestRoa <- as.numeric(round(plmtest(RoaPooling, effect = "time", type = "bp")$p.value, digits = 3))
  PlmtestTobin <- as.numeric(round(plmtest(TobinPooling, effect = "time", type = "bp")$p.value, digits = 3))

  ## Improve p-value understanding
  PlmtestRoa<-ifelse(PlmtestRoa<0.01, paste(PlmtestRoa,"***",sep = ""),
		ifelse(PlmtestRoa<0.05,paste(PlmtestRoa,"**",sep = ""),
		ifelse(PlmtestRoa<0.1,paste(PlmtestRoa,"*",sep = ""), PlmtestRoa)))
  PlmtestTobin<-ifelse(PlmtestTobin<0.01, paste(PlmtestTobin,"***",sep = ""),
		ifelse(PlmtestTobin<0.05,paste(PlmtestTobin,"**",sep = ""),
		ifelse(PlmtestTobin<0.1,paste(PlmtestTobin,"*",sep = ""),PlmtestTobin)))
  
# I test for Fixed Effect Model using pFtest which is a test of individual and/or time effects based on the comparison of the within and the pooling model.
  
  ## Within Model with time effect
  
  RoaWithin <- plm(ROA ~ GS + FirmSize + Leverage + Growth + Industry, data = RoaNoOut, model = "within", effect = "time")
  TobinWithin <- plm(TobinsQ ~ GS + FirmSize + Leverage + Growth + Industry, data = TobinNoOut, model = "within", effect = "time")
  
  ## pFtest
  
  pFtestRoa <- as.numeric(round(pFtest(RoaWithin, RoaPooling)$p.value, digits = 3))
  
  pFtestTobin <- as.numeric(round(pFtest(TobinWithin, TobinPooling)$p.value, digits = 3))
  
  ## Improve p-value understanding
  pFtestRoa<-ifelse(pFtestRoa<0.01, paste(pFtestRoa,"***",sep = ""),
		ifelse(pFtestRoa<0.05,paste(pFtestRoa,"**",sep = ""),
		ifelse(pFtestRoa<0.1,paste(pFtestRoa,"*",sep = ""),pFtestRoa)))
  pFtestTobin<-ifelse(pFtestTobin<0.01, paste(pFtestTobin,"***",sep = ""),
		ifelse(pFtestTobin<0.05,paste(pFtestTobin,"**",sep = ""),
		ifelse(pFtestTobin<0.1,paste(pFtestTobin,"*",sep = ""),pFtestTobin)))

# Let's consolidate into a stargazer table
  
stargazer(TobinPooling, RoaWithin, title = "Green Score - an Alternative Variable for CEP", label = "GreenScoreResults", header = FALSE , font.size = "tiny", omit.stat = "rsq", type = "latex", align = FALSE, single.row = TRUE, model.numbers = FALSE, table.placement = "!", column.labels = c("Model (4)", "Model (5)"), add.lines = list(c("BPLM test (pvalue)", PlmtestTobin, PlmtestRoa),
                           c("F test (pvalue)", pFtestTobin ,pFtestRoa)))


```

----


# Summary

## Main Findings and Contributions

1. Process-based CEP positively influences outcome-based CEP

<!--
- Companies which link the remuneration of any member of a company’s senior executive team with the achievement of environmental performance targets, have a better WatP (+0.022%) and WastP (+0.025%)

- The fact of having a sustainability committee on the board of directors level increases the CaP (+0.058%), WatP (+0.067%) and WastP (+0.046%)

- Companies having their latest reported environmental metrics audited by a third party have a higher CaP (+0.057%), WatP (+0.068%) and WastP (+0.071%)
-->

2. Both process and outcome-based CEP have a positive impact on CFP. This relationship is always positive, no matter the time horizon, and is stronger with a long-term perspective than a short-term perspective.

<!--
#### Regarding process-based CEP variables:

- Companies which link the remuneration of any member of a company’s senior executive team with the achievement of environmental performance targets, are characterized by both a higher long-term CFP (+0.079) and short-term CFP (+0.008). 

- The fact of having a sustainability committee on the board of directors level increases the short-term CFP (+0.012)

- Companies having their latest reported environmental metrics audited by a third party have a higher long-term CFP (+0.158)

#### Regarding outcome-based CEP variables: 

- A 1% increase of carbon productivity increases the short-term CFP (+0.03) and a 1% increase of water productivity increases the long-term CFP (+0.337).

-->

3. Answerr the call of @EndrikatMakingsenseconflicting2014 who highlighted the need for a better understanding of the multidimensionality of both CEP and CFP constructs

----

\begin{frame}[allowframebreaks]
        \frametitle{References}
        \bibliographystyle{amsalpha}
        \bibliography{../bib_files/jabrefmaster.bib}
\end{frame}

\tiny
