---
output:
  pdf_document
---

## Appendix A : Outliers {-}

```{r echo = FALSE, message = FALSE, warning = FALSE, error = FALSE,  results='asis'}

#############################################################
#############################################################
############## Package and DataBase loading #################
#############################################################
#############################################################

rm(list=ls()) #Removes all items in the environment!

#Packages
if (!require("utils")) install.packages("utils")
if (!require("dplyr")) install.packages("dplyr")
if (!require("plm")) install.packages("plm")
if (!require("stargazer")) install.packages("stargazer")
library(stargazer) # to create wonderful tables
library(plm) #to carry out regression
library(utils) #to write database in my folders
library(dplyr) #to play with data

#Database
DB <-as.data.frame(read.csv2("Analysis/DataBase/Lag1_WithCapm.csv", sep = ";",stringsAsFactors=FALSE, header = TRUE))

DB_Lag1 <- DB[,c("Companies",
                 "Year",
                 "Ra",
                 "ROA",
                 "ROE",
                 "TobinsQ",
                 "AlphaJensen",
                 "CarbonProductivity",
                 "WaterProductivity",
                 "WasteProductivity",
                 "EnergyProductivity",
                 "SustainabilityPayLink",
                 "SustainableThemedCommitment",
                 "AuditScore",
                 "FirmSize",
                 "Leverage",
                 "NetMargin",
                 "Industry",
                 "Beta",
                 "CostEquity"
                 )]



```

First I measure the cook's distance of my models. Observations that have a cook’s distance greater than 4 times the mean are considered as influential and are summarized in figures \ref{OutliersRoa}, \ref{OutliersTobinsQ} and \ref{OutliersRoe}. 




<!--Secondly, in order to detect the influence of those outliers, I use the function *outlierTest* from the *car* package [@Fox2012]. This function reports the Bonferroni p-values for Studentized residuals in linear and generalized linear models, based on a t-test for linear models and normal-distribution test for generalized linear models. -->

```{r echo = FALSE, message = FALSE, warning = FALSE, fig.align = 'center', fig.width = 6, fig.height = 6, results = 'asis'}

#############################################################
#############################################################
######## Model without EnergyProductivity as VIF = 5 ########
#############################################################
#############################################################


#####################################
######### Cooks Distance ############
#####################################

# I define my models in lm as cooks.distance do not support plm object
Roa <-lm(ROA ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore + CarbonProductivity + WaterProductivity + WasteProductivity + Leverage + NetMargin + FirmSize + Industry + CostEquity + Beta , data = DB_Lag1)

TobinsQ<-lm(log(TobinsQ) ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore + CarbonProductivity + WaterProductivity + WasteProductivity + Leverage + NetMargin + FirmSize + Industry + CostEquity + Beta , data = DB_Lag1)

Roe <- lm(ROE ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore + CarbonProductivity + WaterProductivity + WasteProductivity + Leverage + NetMargin + FirmSize + Industry+ CostEquity + Beta , data = DB_Lag1)

Jensen <- lm(AlphaJensen ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore + CarbonProductivity + WaterProductivity + WasteProductivity + Leverage + NetMargin + FirmSize + Industry + CostEquity + Beta , data = DB_Lag1)

Return <- lm(Ra ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore + CarbonProductivity + WaterProductivity + WasteProductivity + Leverage + NetMargin + FirmSize + Industry + CostEquity + Beta , data = DB_Lag1)

## I calculate my cooks distance (i.e. D)
cooksdRoa <- cooks.distance(Roa)
cooksdTobinsQ <- cooks.distance(TobinsQ)
cooksdRoe <- cooks.distance(Roe)
cooksdJensen <- cooks.distance(Jensen)
cooksdReturn <- cooks.distance(Return)

## I extract rows considered as influential (observations whose D > 4 * means)

influentialRoa <- as.numeric(names(cooksdRoa)[(cooksdRoa > 4*mean(cooksdRoa, na.rm=T))])  
influentialTobin <- as.numeric(names(cooksdTobinsQ)[(cooksdTobinsQ > 4*mean(cooksdTobinsQ, na.rm=T))])  
influentialRoe <- as.numeric(names(cooksdRoe)[(cooksdRoe > 4*mean(cooksdRoe, na.rm=T))])  
influentialJensen <- as.numeric(names(cooksdJensen)[(cooksdJensen > 4*mean(cooksdJensen, na.rm=T))])  
InfluentialReturn <- as.numeric(names(cooksdReturn)[(cooksdReturn > 4*mean(cooksdReturn, na.rm=T))])  


head(DB_Lag1[influentialRoa, ])  # influential observations 
head(DB_Lag1[influentialTobin, ])  # influential observations 
head(DB_Lag1[influentialRoe, ])  # influential observations 
head(DB_Lag1[influentialJensen, ])  # influential observations 
head(DB_Lag1[InfluentialReturn, ])  # influential observations

#I remove outliers and create three new data frames that I write in my folders

DB_TobinsQ_NoOut <- DB_Lag1[-c(influentialTobin),]
write.csv2(DB_TobinsQ_NoOut, file = "Analysis/DataBase/NoOutliers/Tobins_Lag1_NoOut.csv")

DB_Roa_NoOut <- DB_Lag1[-c(influentialRoa),]
write.csv2(DB_Roa_NoOut, file = "Analysis/DataBase/NoOutliers/Roa_Lag1_NoOut.csv")

DB_Roe_NoOut <- DB_Lag1[-c(influentialRoe),]
write.csv2(DB_Roe_NoOut, file = "Analysis/DataBase/NoOutliers/Roe_Lag1_NoOut.csv")

DB_Jensen_NoOut <- DB_Lag1[-c(influentialJensen),]
write.csv2(DB_Jensen_NoOut, file = "Analysis/DataBase/NoOutliers/Jensen_Lag1_NoOut.csv")

DB_Return_NoOut <- DB_Lag1[-c(InfluentialReturn),]
write.csv2(DB_Return_NoOut, file = "Analysis/DataBase/NoOutliers/Return_Lag1_NoOut.csv")

#########################################################
######### Plm vith new dataset (no outliers) ############
#########################################################

#############################
###### Model 1 : ROA ########
#############################

#Model 1 with outliers with EnergyProductivity
Roa1<-plm(ROA ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore + CarbonProductivity + EnergyProductivity + WaterProductivity + WasteProductivity + Leverage + NetMargin + FirmSize + Industry + CostEquity + Beta , data = DB_Lag1, index = c("Companies", "Year"), model = "random") 

#Model 1 without outliers with EnergyProductivity
Roa2 <-plm(ROA ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore + CarbonProductivity + EnergyProductivity + WaterProductivity + WasteProductivity + Leverage + NetMargin + FirmSize + Industry + CostEquity + Beta  , data = DB_Roa_NoOut, index = c("Companies", "Year"), model = "random") 

#Model 1 with outliers without EnergyProductivity
Roa3 <-plm(ROA ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore + CarbonProductivity + WaterProductivity + WasteProductivity + Leverage + NetMargin + FirmSize + Industry + CostEquity + Beta , data = DB_Lag1, index = c("Companies", "Year"), model = "random") 

#Model 1 without outliers without EnergyProductivity
Roa4 <-plm(ROA ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore + CarbonProductivity + WaterProductivity + WasteProductivity + Leverage + NetMargin + FirmSize + Industry + CostEquity + Beta  , data = DB_Roa_NoOut, index = c("Companies", "Year"), model = "random") 

#Model process-based CEP without outliers

Roa5 <- plm(ROA ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore + Leverage + NetMargin + FirmSize + Industry + CostEquity + Beta  , data = DB_Roa_NoOut, index = c("Companies", "Year"), model = "random") 

#Model outcome-based CEP without outliers

Roa6 <- plm(ROA ~ CarbonProductivity + WaterProductivity + WasteProductivity + Leverage + NetMargin + FirmSize + Industry + CostEquity + Beta  , data = DB_Roa_NoOut, index = c("Companies", "Year"), model = "random")

#############################
#### Model 2 : Tobin's Q ####
#############################

#Mode2 with outliers
Tobins1 <- plm(log(TobinsQ) ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore + CarbonProductivity + WaterProductivity + WasteProductivity + Leverage + NetMargin + FirmSize + Industry + CostEquity + Beta , data = DB_Lag1, index = c("Companies", "Year"), model = "random")

#Mode2 without the 40 outliers from Tobin's Q
Tobins3 <-plm(log(TobinsQ) ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore +  CarbonProductivity + WaterProductivity + WasteProductivity + Leverage + NetMargin + FirmSize + Industry + CostEquity + Beta , data = DB_TobinsQ_NoOut, index = c("Companies", "Year"), model = "random")

#############################
###### Model 3 : ROE ########
#############################

#Mode3 with outliers
Roe1<-plm(ROE ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore + CarbonProductivity + WaterProductivity + WasteProductivity + Leverage + NetMargin + FirmSize + Industry + CostEquity + Beta , data = DB_Lag1, index = c("Companies", "Year"), model = "random") 

#Model3 without the 38 outliers from ROE
Roe2 <-plm(ROE ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore + CarbonProductivity + WaterProductivity + WasteProductivity + Leverage + NetMargin + FirmSize + Industry + CostEquity + Beta , data = DB_Roe_NoOut, index = c("Companies", "Year"), model = "random") 

################################
###### Model 4 : Jensen ########
################################

#Mode4 with outliers
Jensen1<-plm(AlphaJensen ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore + CarbonProductivity + WaterProductivity + WasteProductivity + Leverage + NetMargin + FirmSize + Industry + CostEquity + Beta , data = DB_Lag1, index = c("Companies", "Year"), model = "random") 

#Model4 without outliers 
Jensen2 <-plm(AlphaJensen ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore + CarbonProductivity + WaterProductivity + WasteProductivity + Leverage + NetMargin + FirmSize + Industry + CostEquity + Beta , data = DB_Jensen_NoOut, index = c("Companies", "Year"), model = "random") 

################################
###### Model 5 : Return ########
################################

#Model5 with outliers
Return1<-plm(Ra ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore + CarbonProductivity + WaterProductivity + WasteProductivity + Leverage + NetMargin + FirmSize + Industry + CostEquity + Beta , data = DB_Lag1, index = c("Companies", "Year"), model = "random") 

#Model5 without outliers 
Return2 <-plm(Ra ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore + CarbonProductivity + WaterProductivity + WasteProductivity + Leverage + NetMargin + FirmSize + Industry + CostEquity + Beta , data = DB_Return_NoOut, index = c("Companies", "Year"), model = "random") 

#########################################################
######### My Stargazer's friend do the rest #############
#########################################################


TableRoaEn <- stargazer(Roa1, Roa2, type="latex", label = "Roa1", title = "Model 1 - Energy", header = FALSE)

TableRoaNoEn <- stargazer(Roa3, Roa4, type="latex", label = "Roa2", title = "Model 1 - No Energy", header = FALSE)

TableRoaShort1 <- stargazer(Roa5, type="latex", label = "Roa3", title = "Model 1 - Short Version", header = FALSE)

TableRoaShort2 <- stargazer(Roa6, type="latex", label = "Roa4", title = "Model 1 - Short Version", header = FALSE)

TableTobinsQ <- stargazer(Tobins1, Tobins3, type="latex", label = "Tobin", title = "Model 2 - Comparaison with and without outliers", header = FALSE)

TableRoe <- stargazer(Roe1, Roe2, type="latex", label = "Roe", title = "Model 3 - Comparaison with and without outliers", header = FALSE)

TableJensen <- stargazer(Jensen1, Jensen2, type="latex", label = "Jensen", title = "Model 4 - Comparaison with and without outliers", header = FALSE)

TablkeReturn <- stargazer(Return1, Return2, type="latex", label = "Return", title = "Model 5 - Comparaison with and without outliers", header = FALSE)
```



```{r echo = FALSE, message = FALSE, error = FALSE, warning = FALSE, results = 'asis'}
####################################
######### Hausman Test #############
####################################



#Model without the 2 outliers from ROA
Roa2_Fixed <-plm(ROA ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore + CarbonProductivity + WaterProductivity + WasteProductivity + Leverage + NetMargin + FirmSize + Industry + CostEquity + Beta  , data = DB_Roa_NoOut, index = c("Companies", "Year"), model = "within") 

#Mode2 without the 40 outliers from Tobin's Q
Tobins3_Fixed <-plm(log(TobinsQ) ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore +  CarbonProductivity + WaterProductivity + WasteProductivity + Leverage + NetMargin + FirmSize + Industry + CostEquity + Beta , data = DB_TobinsQ_NoOut, index = c("Companies", "Year"), model = "within")

#Model3 without the 38 outliers from ROE
Roe2_Fixed <-plm(ROE ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore + CarbonProductivity + WaterProductivity + WasteProductivity + Leverage + NetMargin + FirmSize + Industry + CostEquity + Beta  , data = DB_Roe_NoOut, index = c("Companies", "Year"), model = "within") 

#Model4 without outliers 
Jensen2_Fixed <-plm(AlphaJensen ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore + CarbonProductivity + WaterProductivity + WasteProductivity + Leverage + NetMargin + FirmSize + Industry + CostEquity + Beta  , data = DB_Jensen_NoOut, index = c("Companies", "Year"), model = "within") 

#Model5 without outliers 
Return2_Fixed <-plm(Ra ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore + CarbonProductivity + WaterProductivity + WasteProductivity + Leverage + NetMargin + FirmSize + Industry + CostEquity + Beta  , data = DB_Return_NoOut, index = c("Companies", "Year"), model = "within") 




HausmannRoa <-  cbind("Model 1 without outliers",round(phtest(Roa2_Fixed,Roa2)$p.value,4))
HausmannTobinsQ <-  cbind("Model 2 without outliers",round(phtest(Tobins3_Fixed,Tobins3)$p.value,4))
HausmannRoe <-  cbind("Model 3 without outliers",round(phtest(Roe2_Fixed,Roe2)$p.value,4))
HausmannJensen <-  cbind("Model 4 without outliers",round(phtest(Jensen2_Fixed,Jensen2)$p.value,4))
HausmannReturn <-  cbind("Model 5 without outliers",round(phtest(Return2_Fixed,Return2)$p.value,4))



HausmanTable <- rbind(HausmannRoa, HausmannTobinsQ, HausmannRoe, HausmannReturn)
colnames(HausmanTable) <- c("Model","P-Value")

stargazer(HausmanTable, summary = FALSE, table.placement = "h", type="latex", label = "Hausman", title = "Hausman Test PValue", header = FALSE)

#######################################################
######### Vizualisation Fixed Effect Test #############
#######################################################

stargazer(Roa2_Fixed, Tobins3_Fixed, Roe2_Fixed, summary = FALSE, table.placement = "h", type="latex", label = "Fix", title = "Fixed Effect Model - NoOutlier NoEnergy (1/2)", header = FALSE)

stargazer(Return2_Fixed, Jensen2_Fixed, summary = FALSE, table.placement = "h", type="latex", label = "Fix2", title = "Fixed Effect Model - NoOutlier NoEnergy (2/2)", header = FALSE)



```



```{r echo = FALSE, message = FALSE, error = FALSE, warning = FALSE, results = 'asis'}

#######################################################
######### Vizualisation best random Effect ############
#######################################################

stargazer(Roa4, Roe2, summary = FALSE, table.placement = "h", type="latex", label = "BestRm1", title = "Best RE Model - No out 1/2 ", header = FALSE)

stargazer(Tobins3, Return2,Jensen2, summary = FALSE, table.placement = "h", type="latex", label = "BestRm2", title = "Best RE Model - No out 2/2", header = FALSE)
```


```{r echo = FALSE, message = FALSE, error = FALSE, warning = FALSE, results = 'hide'}

#############################################################
######### Tests for individual and time effects #############
#############################################################

#I need pooling Model for this test

#Model without the 2 outliers from ROA
Roa2_Pooling <-plm(ROA ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore + CarbonProductivity + WaterProductivity + WasteProductivity + Leverage + NetMargin + FirmSize + Industry + CostEquity  , data = DB_Roa_NoOut, index = c("Companies", "Year"), model = "pooling") 

#Mode2 without the 40 outliers from Tobin's Q
Tobins3_Pooling <-plm(TobinsQ ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore +  CarbonProductivity + WaterProductivity + WasteProductivity + Leverage + NetMargin + FirmSize + Industry + CostEquity , data = DB_TobinsQ_NoOut, index = c("Companies", "Year"), model = "pooling")

#Model3 without the 38 outliers from ROE
Roe2_Pooling <-plm(ROE ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore + CarbonProductivity + WaterProductivity + WasteProductivity + Leverage + NetMargin + FirmSize + Industry + CostEquity  , data = DB_Roe_NoOut, index = c("Companies", "Year"), model = "pooling") 

# PlmTest

PlmTestRoa <- cbind("Model 1 without outliers",round(plmtest(Roa2_Pooling, effect = "twoways", type = "bp")$p.value,4))
PlmTestTobinsQ <- cbind("Model 2 without outliers",round(plmtest(Tobins3_Pooling, effect = "twoways", type = "bp")$p.value,4))
PlmTestRoe <- cbind("Model 3 without outliers",round(plmtest(Roe2_Pooling, effect = "twoways", type = "bp")$p.value,4))

PlmTestTable <- rbind(PlmTestRoa, PlmTestTobinsQ, PlmTestRoe)
colnames(PlmTestTable) <- c("Model","P-Value")

stargazer(PlmTestTable, summary = FALSE, table.placement = "h", type="latex", label = "PlmTest", title = "Twoways effect Test PValue", header = FALSE)

################################################################
######### Twoways effect significant - Redo models #############
################################################################

########Something goes wrong....

#Pvalue < 0.05 then twoway effect is significant and I add twoway effect to my models

#Model without the 2 outliers from ROA
#Roa2_Twoways <-plm(ROA ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore + CarbonProductivity + WaterProductivity + WasteProductivity + Leverage + NetMargin + FirmSize + Industry + Beta  , data = DB_Roa_NoOut, index = c("Companies", "Year"), model = "random", effect = "twoways") 

#Mode2 without the 40 outliers from Tobin's Q
#Tobins3_Twoways <-plm(TobinsQ ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore +  CarbonProductivity + WaterProductivity + WasteProductivity + Leverage + NetMargin + FirmSize + Industry + Beta , data = DB_TobinsQ_NoOut, index = c("Companies", "Year"), model = "random")

#Model3 without the 38 outliers from ROE
#Roe2_Twoways <-plm(ROE ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore + CarbonProductivity + WaterProductivity + WasteProductivity + Leverage + NetMargin + FirmSize + Industry + Beta  , data = DB_Roe_NoOut, index = c("Companies", "Year"), model = "random", effect = "twoways") 

#stargazer(Roa2_Twoways, Tobins3_Twoways, Roe2_Twoways, summary = FALSE, table.placement = "h", type="latex", label = "TwoWays", title = "Model with twoways effect (NoOutliers and NoEnergy)", header = FALSE)

```




\begin{figure}[ht]
\caption{Observations considered as outliers in model 1 (i.e. Roa)}
\label{OutliersRoa}
```{r echo = FALSE, message = FALSE, warning = FALSE, fig.align = 'center', fig.width = 6, fig.height = 6, results = 'asis'}

#Model Roa
## I summarise on a graph, those observations that have a cook’s distance greater than 4 times the mean and which may be considered as outliers
plot(cooksdRoa, pch="*", cex=2)  # plot cook's distance
abline(h = 4*mean(cooksdRoa, na.rm=T), col="red")  # add cutoff line
text(x=1:length(cooksdRoa)+1, y=cooksdRoa, labels=ifelse(cooksdRoa>4*mean(cooksdRoa, na.rm=T),names(cooksdRoa),""), col="red")  # add labels
```
\end{figure}



\begin{figure}[ht]
\caption{Observations considered as outliers in model 2 (i.e. Tobin's Q)}
\label{OutliersTobinsQ}
```{r echo = FALSE, message = FALSE, warning = FALSE, fig.align = 'center', fig.width = 6, fig.height = 6, results = 'asis'}


#Model TobinsQ
plot(cooksdTobinsQ, pch="*", cex=2)  

abline(h = 4*mean(cooksdTobinsQ, na.rm=T), col="red")  # add cutoff line
text(x=1:length(cooksdTobinsQ)+1, y=cooksdTobinsQ, labels=ifelse(cooksdTobinsQ>4*mean(cooksdTobinsQ, na.rm=T),names(cooksdTobinsQ),""), col="red")  # add labels

```
\end{figure}


\begin{figure}[ht]
\caption{Observations considered as outliers in model 1 (i.e. Roe)}
\label{OutliersRoe}
```{r echo = FALSE, message = FALSE, warning = FALSE, fig.align = 'center', fig.width = 6, fig.height = 6, results = 'asis'}

#Model Roe
## I summarise on a graph, those observations that have a cook’s distance greater than 4 times the mean and which may be considered as outliers
plot(cooksdRoe, pch="*", cex=2)  # plot cook's distance
abline(h = 4*mean(cooksdRoe, na.rm=T), col="red")  # add cutoff line
text(x=1:length(cooksdRoe)+1, y=cooksdRoe, labels=ifelse(cooksdRoe>4*mean(cooksdRoe, na.rm=T),names(cooksdRoe),""), col="red")  # add labels
```
\end{figure}


\begin{figure}[ht]
\caption{Observations considered as outliers in model 4 (i.e. Jensen's Alpha)}
\label{OutliersJensen}
```{r echo = FALSE, message = FALSE, warning = FALSE, fig.align = 'center', fig.width = 6, fig.height = 6, results = 'asis'}

#Model Jensen
## I summarise on a graph, those observations that have a cook’s distance greater than 4 times the mean and which may be considered as outliers
plot(cooksdJensen, pch="*", cex=2)  # plot cook's distance
abline(h = 4*mean(cooksdJensen, na.rm=T), col="red")  # add cutoff line
text(x=1:length(cooksdJensen)+1, y=cooksdJensen, labels=ifelse(cooksdJensen>4*mean(cooksdJensen, na.rm=T),names(cooksdJensen),""), col="red")  # add labels
```
\end{figure}

\begin{figure}[ht]
\caption{Observations considered as outliers in model 5 (i.e.Compounded Returns)}
\label{OutliersReturn}
```{r echo = FALSE, message = FALSE, warning = FALSE, fig.align = 'center', fig.width = 6, fig.height = 6, results = 'asis'}

#Model Jensen
## I summarise on a graph, those observations that have a cook’s distance greater than 4 times the mean and which may be considered as outliers
plot(cooksdReturn, pch="*", cex=2)  # plot cook's distance
abline(h = 4*mean(cooksdReturn, na.rm=T), col="red")  # add cutoff line
text(x=1:length(cooksdReturn)+1, y=cooksdReturn, labels=ifelse(cooksdReturn>4*mean(cooksdReturn, na.rm=T),names(cooksdReturn),""), col="red")  # add labels
```
\end{figure}
