---
output: 
  pdf_document:
    fig_caption: yes
    number_sections: yes
    highlight: haddock
bibliography: References.bib
csl: CSL/elsevier-harvard.csl
link-citations: yes
fontsize: 12pt
geometry: margin = 1.2in
urlcolor: red
linkcolor: red
citecolor: blue
indent: true
nocite: | 
  @Hlavac2018
header-includes:
- \usepackage{placeins}
- \usepackage{hyperref}
- \usepackage{fancyhdr}
- \usepackage{setspace}
- \usepackage{chngcntr}
- \onehalfspacing
- \counterwithin{figure}{section}
- \counterwithin{table}{section}
- \usepackage{rotating}
- \usepackage{dcolumn}
---


<!-- The following latex function avoid that footnotes are splited up accros two pages-->

\interfootnotelinepenalty=10000 

```{r echo = FALSE, warning = FALSE, message = FALSE}
rm(list=ls()) #Removes all items in Environment!
```

\pagenumbering{gobble} 

```{r child = 'UnamurCoverpage.Rmd'}
```

\newpage

\pagenumbering{roman}
```{r child = 'Abstract.Rmd'}
```

\newpage
```{r child = 'AuthorNote.Rmd'}
```

\newpage
```{r child = 'Acknowledgments.Rmd'}
```

\newpage
\renewcommand{\contentsname}{Table of Contents}
\setcounter{tocdepth}{3}
\tableofcontents

\newpage
\addcontentsline{toc}{section}{List of Tables}
\listoftables
\addcontentsline{toc}{section}{List of Figures}
\listoffigures

\newpage
```{r child = 'Abbreviations.Rmd'}
```

\newpage
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0pt}

\pagenumbering{arabic}
\fancyhead[CO,CE]{Introduction}
```{r child = 'Introduction.Rmd'} 
```

\FloatBarrier
\newpage
\fancyhead[CO,CE]{Literature Review}
```{r child = 'LiteratureReview.Rmd'} 
```

\FloatBarrier
\newpage
\fancyhead[CO,CE]{Data Description}
```{r child = 'DataDescription.Rmd'} 
```

\FloatBarrier
\newpage
\fancyhead[CO,CE]{Methodology}
```{r child = 'Methodology.Rmd'} 
```


\FloatBarrier
\newpage
\fancyhead[CO,CE]{Results}
```{r child = 'Results.Rmd'} 
```

\FloatBarrier
\newpage
\fancyhead[CO,CE]{Sensitivity Analysis}
```{r child = 'SensitivityAnalysis.Rmd'} 
```

\FloatBarrier
\newpage
\fancyhead[CO,CE]{Discussion}
```{r child = 'Discussion.Rmd'} 
```

\FloatBarrier
\newpage
\fancyhead[CO,CE]{Conclusion}
```{r child = 'Conclusion.Rmd'} 
```

\newpage
\fancyhead[CO,CE]{Appendices}
```{r child = 'Appendix.Rmd'} 
```

\newpage
\fancyhead[CO,CE]{References}

# References {-}
\noindent