---
output: 
  pdf_document:
    fig_caption: yes
    number_sections: yes
bibliography: References.bib
#csl:
fontsize: 12pt
geometry: margin = 1.2in
urlcolor: blue
linkcolor: blue
citecolor: blue
header-includes:
- \usepackage{placeins}
- \usepackage{fancyhdr}
- \usepackage{setspace}
- \usepackage{chngcntr}
- \onehalfspacing
- \counterwithin{figure}{section}
- \counterwithin{table}{section}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.path = '/figures/',
                      echo = FALSE, warning = FALSE, message = FALSE)

# Code chunks option applied to the whole document
```

```{r echo = FALSE, warning = FALSE, message = FALSE}
rm(list=ls()) #Removes all items in Environment!
if (!require("utils")) install.packages("utils")
if (!require("dplyr")) install.packages("dplyr")
if (!require("plm")) install.packages("plm")

library(plm)
library(utils)
library(dplyr)

# I dowload my DB with read.csv2
DB_Lag1<-data.frame(read.csv2("Analysis/DataBase/Lag_1.csv", sep = ";",stringsAsFactors=FALSE, header = TRUE ))

```

\pagenumbering{gobble} 

```{r child = 'Coverpage.Rmd'}
```


\newpage
\pagestyle{fancy}

\fancyhead[LE,RO]{}
\fancyhead[LO,RE]{}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0pt}

\pagenumbering{roman}

\fancyhead[CO,CE]{Abstract}

```{r child = 'Abstract.Rmd'}
```

\newpage
\fancyhead[CO,CE]{Acknowledgements}

```{r child = 'Acknowledgments.Rmd'}
```

\newpage
\fancyhead[CO,CE]{Table of Contents}
\setcounter{tocdepth}{3}
\tableofcontents

\newpage
\fancyhead[CO,CE]{List of Tables}
\addcontentsline{toc}{section}{List of Tables}
\listoftables

\newpage
\fancyhead[CO,CE]{List of Figures}
\addcontentsline{toc}{section}{List of Figures}
\listoffigures

\newpage
\pagenumbering{arabic}
\fancyhead[CO,CE]{Introduction}
```{r child = 'Introduction.Rmd'} 
```

\FloatBarrier
\newpage
\fancyhead[CO,CE]{Literature Review}
```{r child = 'LiteratureReview.Rmd'} 
```

\FloatBarrier
\newpage
\fancyhead[CO,CE]{Hypotheses}
```{r child = 'Hypotheses.Rmd'} 
```

\FloatBarrier
\newpage
\fancyhead[CO,CE]{Data Description}
```{r child = 'DataDescription.Rmd'} 
```

\FloatBarrier
\newpage
\fancyhead[CO,CE]{Methodology}
```{r child = 'Methodology.Rmd'} 
```


\FloatBarrier
\newpage
\fancyhead[CO,CE]{Results}
```{r child = 'Results.Rmd'} 
```

\FloatBarrier
\newpage
\fancyhead[CO,CE]{Discussion}
```{r child = 'Discussion.Rmd'} 
```

\FloatBarrier
\newpage
\fancyhead[CO,CE]{Conclusion}
```{r child = 'Conclusion.Rmd'} 
```

\newpage
\fancyhead[CO,CE]{Appendix}
```{r child = 'Appendix.Rmd'} 
```

\newpage
\fancyhead[CO,CE]{References}

# References
