---
output:
  pdf_document
---

## Appendix A : Outliers {-}
```{r echo = FALSE, message = FALSE, warning = FALSE,  results='asis'}
#Packages
if (!require("utils")) install.packages("utils")
if (!require("car")) install.packages("car")
if (!require("dplyr")) install.packages("dplyr")
if (!require("plm")) install.packages("plm")
if (!require("stargazer")) install.packages("stargazer")
library(stargazer)
library(plm)
library(utils)
library(car)
library(dplyr)

#Database
DB_Lag2<-as.data.frame(read.csv2("DataBase/Lag_2.csv", sep = ";",stringsAsFactors=FALSE, header = TRUE ))

```

First I measure the cook's distance of my models. Observations that have a cook’s distance greater than 4 times the mean are considered as influential and are summarized in figures \ref{OutliersRoa}, \ref{OutliersTobinsQ} and \ref{OutliersRoe}. 




<!--Secondly, in order to detect the influence of those outliers, I use the function *outlierTest* from the *car* package [@Fox2012]. This function reports the Bonferroni p-values for Studentized residuals in linear and generalized linear models, based on a t-test for linear models and normal-distribution test for generalized linear models. -->

```{r echo = FALSE, message = FALSE, warning = FALSE, fig.align = 'center', fig.width = 6, fig.height = 6, results = 'asis'}

#############################################################
#############################################################
######## Model without EnergyProductivity as VIF = 5 ########
#############################################################
#############################################################


#####################################
######### Cooks Distance ############
#####################################

# I define my models in lm as cooks.distance do not support plm object
Roa <-lm(ROA ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore + CarbonProductivity + WaterProductivity + WasteProductivity + Leverage + NetMargin + FirmSize , data = DB_Lag2)

TobinsQ<-lm(TobinsQ ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore + CarbonProductivity + WaterProductivity + WasteProductivity + Leverage + NetMargin + FirmSize , data = DB_Lag2)

Roe <- lm(TobinsQ ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore + CarbonProductivity + WaterProductivity + WasteProductivity + Leverage + NetMargin + FirmSize , data = DB_Lag2)

## I calculate my cooks distance (i.e. D)
cooksdRoa <- cooks.distance(Roa)
cooksdTobinsQ <- cooks.distance(TobinsQ)
cooksdRoe <- cooks.distance(Roe)

## I extract rows considered as influential (observations whose D > 4 * means)

influentialRoa <- as.numeric(names(cooksdRoa)[(cooksdRoa > 4*mean(cooksdRoa, na.rm=T))])  
influentialTobin <- as.numeric(names(cooksdTobinsQ)[(cooksdTobinsQ > 4*mean(cooksdTobinsQ, na.rm=T))])  
influentialRoe <- as.numeric(names(cooksdRoe)[(cooksdRoe > 4*mean(cooksdRoe, na.rm=T))])  

head(DB_Lag2[influentialRoa, ])  # influential observations - number = 2 
head(DB_Lag2[influentialTobin, ])  # influential observations - number = 40
head(DB_Lag2[influentialRoe, ])  # influential observations - number = 38


#I remove outliers and create three new data frames

DB_Lag2_NoOutliers <- DB_Lag2[-c(influentialTobin,influentialRoa),]
DB_Roa_NoOut <- DB_Lag2[-c(influentialRoa),]
DB_Roe_NoOut <- DB_Lag2[-c(influentialRoe),]


#########################################################
######### Plm vith new dataset (no outliers) ############
#########################################################

#############################
###### Model 1 : ROA ########
#############################

#Model with outliers
Roa1<-plm(ROA ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore + CarbonProductivity + WaterProductivity + WasteProductivity + Leverage + NetMargin + FirmSize , data = DB_Lag2, index = c("Companies", "YearFinancialIndicator"), model = "random") 

#Model without the 2 outliers from ROA
Roa2 <-plm(ROA ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore + CarbonProductivity + WaterProductivity + Leverage + NetMargin + FirmSize  , data = DB_Roa_NoOut, index = c("Companies", "YearFinancialIndicator"), model = "random") 

#Model without the 42 outliers from both Tobin's Q and ROA
Roa3 <-plm(ROA ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore + CarbonProductivity + WaterProductivity + WasteProductivity + Leverage + NetMargin + FirmSize , data = DB_Lag2_NoOutliers, index = c("Companies", "YearFinancialIndicator"), model = "random") 


#############################
#### Model 2 : Tobin's Q ####
#############################

#Mode2 with outliers
Tobins1 <- plm(TobinsQ ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore + CarbonProductivity + WaterProductivity + WasteProductivity + Leverage + NetMargin + FirmSize , data = DB_Lag2, index = c("Companies", "YearFinancialIndicator"), model = "random")

#Mode2 without the 40 outliers from Tobin's Q
Tobins3 <-plm(TobinsQ ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore +  CarbonProductivity + WaterProductivity + WasteProductivity + Leverage + NetMargin + FirmSize , data = DB_Lag2_NoOutliers, index = c("Companies", "YearFinancialIndicator"), model = "random")

#############################
###### Model 3 : ROE ########
#############################

#Mode3 with outliers
Roe1<-plm(ROE ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore + CarbonProductivity + WaterProductivity + WasteProductivity + Leverage + NetMargin + FirmSize , data = DB_Lag2, index = c("Companies", "YearFinancialIndicator"), model = "random") 

#Model3 without the 38 outliers from ROE
Roe2 <-plm(ROE ~ SustainabilityPayLink + SustainableThemedCommitment + AuditScore + CarbonProductivity + WaterProductivity + Leverage + NetMargin + FirmSize  , data = DB_Roe_NoOut, index = c("Companies", "YearFinancialIndicator"), model = "random") 


#########################################################
######### My Stargazer's friend do the rest #############
#########################################################


TableRoa <- stargazer(Roa1, Roa2, Roa3, type="latex", label = "Roa", title = "Model 1 - Comparaison with and without outliers", header = FALSE)

TableTobinsQ <- stargazer(Tobins1, Tobins3, type="latex", label = "Tobin", title = "Model 2 - Comparaison with and without outliers", header = FALSE)

TableRoa <- stargazer(Roe1, Roe2, type="latex", label = "Roe", title = "Model 3 - Comparaison with and without outliers", header = FALSE)
```






\begin{figure}[ht]
\caption{Observations considered as outliers in model 1 (i.e. Roa)}
\label{OutliersRoa}
```{r echo = FALSE, message = FALSE, warning = FALSE, fig.align = 'center', fig.width = 6, fig.height = 6, results = 'asis'}

#Model Roa
## I summarise on a graph, those observations that have a cook’s distance greater than 4 times the mean and which may be considered as outliers
plot(cooksdRoa, pch="*", cex=2)  # plot cook's distance
abline(h = 4*mean(cooksdRoa, na.rm=T), col="red")  # add cutoff line
text(x=1:length(cooksdRoa)+1, y=cooksdRoa, labels=ifelse(cooksdRoa>4*mean(cooksdRoa, na.rm=T),names(cooksdRoa),""), col="red")  # add labels
```
\end{figure}



\begin{figure}[ht]
\caption{Observations considered as outliers in model 2 (i.e. Tobin's Q)}
\label{OutliersTobinsQ}
```{r echo = FALSE, message = FALSE, warning = FALSE, fig.align = 'center', fig.width = 6, fig.height = 6, results = 'asis'}


#Model TobinsQ
plot(cooksdTobinsQ, pch="*", cex=2)  

abline(h = 4*mean(cooksdTobinsQ, na.rm=T), col="red")  # add cutoff line
text(x=1:length(cooksdTobinsQ)+1, y=cooksdTobinsQ, labels=ifelse(cooksdTobinsQ>4*mean(cooksdTobinsQ, na.rm=T),names(cooksdTobinsQ),""), col="red")  # add labels

```
\end{figure}


\begin{figure}[ht]
\caption{Observations considered as outliers in model 1 (i.e. Roe)}
\label{OutliersRoe}
```{r echo = FALSE, message = FALSE, warning = FALSE, fig.align = 'center', fig.width = 6, fig.height = 6, results = 'asis'}

#Model Roe
## I summarise on a graph, those observations that have a cook’s distance greater than 4 times the mean and which may be considered as outliers
plot(cooksdRoe, pch="*", cex=2)  # plot cook's distance
abline(h = 4*mean(cooksdRoe, na.rm=T), col="red")  # add cutoff line
text(x=1:length(cooksdRoe)+1, y=cooksdRoe, labels=ifelse(cooksdRoe>4*mean(cooksdRoe, na.rm=T),names(cooksdRoe),""), col="red")  # add labels
```
\end{figure}
