---
title: "DataBase Documentation"
author: "Kinif Pierrick"
date: "26 mars 2018"
output: pdf_document
---

```{r echo = FALSE, warning = FALSE, message = FALSE}
rm(list=ls()) #Removes all items in Environment!
if (!require("utils")) install.packages("utils")
if (!require("dplyr")) install.packages("dplyr")
if (!require("plm")) install.packages("plm")

library(plm)
library(utils)
library(dplyr)

# The excel file contains several sheets with all my data
# The csv file contains only variables of my model. Hence I dowload my DB with read.csv2
DB_Roa<-data.frame(read.csv2("DataBase_010418.csv", sep = ";",stringsAsFactors=FALSE, header = TRUE ))
write.csv2(DB_Roa, file = "DB_Roa.csv")
## This DB will be used for analysis with my dependent variable = ROA

# From DB I select only row where TobinsQ <> zero . This database will be used when my dependent variable = TobinsQ

DB_Tobin <- filter(DB_Roa, !is.na(TobinsQ))
write.csv2(DB_Tobin, file = "DB_Tobin.csv")
```



This section give you an overview of my database. The \autoref{Smpl} contains a sample of my database. The \autoref{VarDef} desribes my variables.  




```{r echo = FALSE, message = FALSE, warning = FALSE,  results='asis'}
if (!require("stargazer")) install.packages("stargazer")
library(stargazer)

if (!require("plm")) install.packages("plm")
library(plm)

PanelData <- pdata.frame(DB_Roa, index=c("Companies", "YearFinancialIndicator"))
smpl <- PanelData[c(1:10),c(1:4)]
stargazer(PanelData[c(1:10),c(1:4)], summary = FALSE, type="latex", title = "Sample selection of the data base", label="Smpl", table.placement = "h", digits = 2, header = FALSE) # the agument 'header = FALSE" is really important to remove the citation info of stargazer package"

```



Function *pdim()* extracts the dimensions of the panel data:



```{r echo = TRUE}
library(plm)
pdim(DB_Roa)
pdim(DB_Tobin)
```


\begin{table}[h]
\centering
\caption{Variable Definition} 
\label{VarDef}
\begin{tabular}{llp{8cm}}
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & Variables & Description \\ 
\hline
1 & Tobin's Q & The ratio of a firm’s market value to the replacement cost of its assets \\ 
2 & Return on Asset & Earnings before interest over total firm assets \\ 
3 & Energy Productivity & Revenue (\$US) / Total Energy Consumption \\ 
4 & Carbon Productivity & Revenue (\$US) / Total Greenhouse gas Emissions (CO2) \\ 
5 & Water Productiviry & Revenue (\$US) / Total water (m3) \\ 
6 & Waste Productivity & Revenue (\$US) / [Total waste generated (metric tonnes)–waste recycled/reused (tones)] \\ 
7 & Sustainability Pay Link & A mechanism to link the remuneration of any member of a company's senior executive team with the achievement of environmental performance targets. The existence of such a link is awarded a score of 100\%. A score of 0\% is attributed if there is no such mechanism in place \\ 
8 & Sustainable Themed Commitment & Refers to the existence of a committee at the Board of Directors level whose mandate is related to the sustainability of the company, including but not limited to environmental matters. A score of 100\% accrues to the company when such link exists and a score of 0\% is attributed if there is no such link in place \\ 
9 & Audit Score & Refers to the case where a company provides evidence that the latest reported environmental metrics were audited by a third party. Newsweek and their research partners award a score of 100\% if such audit has been performed, and a score of 0\% is given when such audit was not performed. \\ 
10 & Leverage & Log of the square of the ratio of long-term debt to common shareholders' equity (shareholders equity minus preferred equity) \\ 
11 & Net Margin & Log of the ratio of earnings to revenue \\ 
12 & Firm Size & Log of total assets \\ 
13 & Industry & Global Industry Classification Standard (GICS) of the firm. The variable take a value from 1 to 10 where 1 = Consumer Discretionary, 2 = Consumer Staples, 3 = Energy, 4 = Financials, 5 = Health Care, 6 = Industrials, 7 = Information Technology, 8 = Materials, 9 = Pharmaceuticals / Biotechnology, 10 = Telecommunication Services and 11 = Utilities \\ 
\hline
\end{tabular}
\end{table}