---
title: "DataBase Documentation"
author: "Kinif Pierrick"
date: "26 mars 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Introduction

The goal of this pdf document is threefold. Firstly I give a description of the database and explain how I built it. Secondly it aims at getting a handle on the data. Lastly I describe each variables. 

# Database Description



# Get a handle on my data

First, let me import my database.For this I use the `read.table` function from the `utils` package  [@HenrikBengtsson2017]. 

```{r}
library(utils)
DataBase<-data.frame(read.table("DataBase_26032018.csv", sep = ";", header = TRUE ))
```

The `dim` function shows that the database contains `r nrow(DataBase)` rows and `r ncol(DataBase)` variables.

```{r}
dim(DataBase)
```

Let's have a closer look on the database in using the `names` and `head` function. The first one lists name of each variable whereas the second one returns the first lines of the database. 

```{r echo=FALSE}
names(DataBase)
head(DataBase[, 1:5])
```


#Reference
